% chapters/chapter1/exercises/sec2_en_exercises.tex
%
% Exercises for Chapter 1, Section 2.
% This file is intentionally left as a placeholder for the section author.
%
% Suggested structure:
% \section*{Exercises}
% \addcontentsline{toc}{section}{Exercises}
%
% \begin{enumerate}[label=\textbf{Exercise 1.\arabic*.}, leftmargin=*]
%     \item ...
% \end{enumerate}

\subsection*{Section 1.2}

\noindent
The exercises in this section focus on the system-level value of ISAC, with particular
emphasis on understanding ``system capability restructuring,'' ``system-level benefit
restructuring,'' and the core values of spectrum efficiency, hardware cost, deployment
efficiency, and business closed-loop capability. Readers are encouraged to complete
them independently after studying this section. Some of these exercises may also be
used for classroom discussion or course assignments.

\begin{enumerate}[label=\textbf{\arabic*.}, leftmargin=*]

    \item \textit{(Conceptual Understanding)} Why is ISAC not merely an ``optional addition of functions,'' but a restructuring of system capability? Explain your answer by comparing ``standalone communication systems,'' ``standalone sensing systems,'' and ``integrated systems.''

    \item \textit{(Conceptual Understanding)} This section argues that the core value of ISAC does not lie in the improvement of a single pointwise performance metric, but in the restructuring of system-level benefits. Explain the meaning of ``system-level benefit restructuring,'' and clarify how it differs fundamentally from ``having one better metric.''

    \item \textit{(Conceptual Understanding)} Why is the design objective of traditional communication systems mainly oriented toward information transmission rather than environmental-state acquisition, such that they often appear to be ``unaware of the physical world'' at the service level? Why was this limitation less pronounced before 5G, but is becoming increasingly evident in the 6G era? Illustrate your answer with specific application scenarios.

    \item \textit{(Comparative Analysis)} Compare the following two deployment schemes from the perspectives of:
    \begin{enumerate}[label=(\alph*)]
        \item spectrum occupation mode;
        \item hardware construction cost;
        \item deployment procedure and implementation complexity;
        \item service support capability.
    \end{enumerate}
    Then analyze which scheme is more suitable for large-scale emerging 6G scenarios:
    \begin{enumerate}[label=(\roman*)]
        \item standalone deployment of communication and sensing systems;
        \item integrated deployment using ISAC.
    \end{enumerate}

    \item \textit{(Comparative Analysis)} This section analyzes the core value of ISAC from four aspects: spectrum efficiency, hardware cost, deployment efficiency, and business closed-loop capability. Are these four types of value independent of each other? If not, analyze their possible coupling relationships and mutual reinforcement mechanisms.

    \item \textit{(Comparative Analysis)} Improved spectrum efficiency does not mean that ``ISAC is always superior to standalone systems in every scenario.'' Based on the following factors, analyze the applicable conditions and boundaries under which ISAC spectral gain holds:
    \begin{enumerate}[label=(\alph*)]
        \item resource conflicts between the two functions;
        \item mutual interference and self-interference;
        \item target-resolution requirements;
        \item communication-link quality requirements.
    \end{enumerate}

    \item \textit{(In-Depth Thinking and Discussion)} Suppose a city plans to build vehicle--road collaborative infrastructure, with two candidate schemes:

    Scheme A: separately build communication base stations and roadside radar;

    Scheme B: upgrade communication base stations with ISAC capability.

    Compare the two schemes from the perspectives of CAPEX, OPEX, deployment cycle, maintenance complexity, and future service expansion capability, and then provide your recommendation.

    \item \textit{(In-Depth Thinking and Discussion)} This section points out that ISAC can reduce total system cost by sharing hardware resources such as antenna arrays, RF chains, and baseband processing platforms. Reflect on the following question: although communication and sensing do not have perfectly aligned requirements in terms of dynamic range, linearity, clock precision, and transmit--receive isolation, why can hardware sharing still be more economical overall in many scenarios? Discuss this from the perspective of ``total system cost'' rather than ``single-module optimal performance.''

    \item \textit{(In-Depth Thinking and Discussion)} With respect to the value of ``deployment efficiency,'' answer the following:
    \begin{enumerate}[label=(\alph*)]
        \item Why is ISAC particularly suitable for emerging scenarios such as the low-altitude economy, industrial Internet, and public safety, where rapid, wide-area, and large-scale deployment is required?
        \item If these scenarios rely entirely on standalone sensing infrastructure, what practical deployment obstacles may arise?
    \end{enumerate}

    \item \textit{(In-Depth Thinking and Discussion)} This section proposes that one of the greatest values of ISAC lies in forming a business closed loop of ``perception--transmission--decision--feedback.'' Choose one of the following scenarios for analysis: vehicle--road coordination, low-altitude UAV management, smart factories, or public-safety monitoring. Explain:
    \begin{enumerate}[label=(\alph*)]
        \item what information is obtained during the sensing stage;
        \item what content is transmitted during the communication stage;
        \item who performs the decision-making;
        \item how the feedback affects the next round of system behavior.
    \end{enumerate}

    \item \textit{(In-Depth Thinking and Discussion)} One viewpoint argues: ``As long as some radar devices or sensors are externally attached to a communication system, environmental sensing can also be achieved, so there is no need to develop ISAC.'' Critically discuss this viewpoint based on the content of this section. Your discussion should cover at least the following three aspects:
    \begin{enumerate}[label=(\alph*)]
        \item system cost;
        \item deployment efficiency;
        \item business closed-loop capability.
    \end{enumerate}

    \item \textit{(In-Depth Thinking and Discussion)} Discuss why business closed-loop capability is the key for ISAC to become an intrinsic 6G capability, rather than merely an additional advantage. Hint: your discussion may consider changes in the role of the network, the demand for intelligence, digital twins, and the integration of communication, sensing, computation, and control.

    \item \textit{(In-Depth Thinking and Discussion)} Suppose that future 6G networks are widely equipped with ISAC capability. How might the role of operators change? Will they still mainly act as ``connectivity service providers,'' or will they further evolve into ``environmental information service providers'' or even ``decision-support platforms''? Explain your understanding.

    \item \textit{(Open Exploration)} If you were a system designer and needed to evaluate the practical value of ISAC for a certain application scenario, along what dimensions would you construct an evaluation framework? Provide at least five evaluation dimensions, and explain which core value of ISAC each dimension corresponds to. When building the evaluation framework, try to balance technical performance, deployment cost, and service value.

    \item \textit{(Open Exploration)} In your view, in which industries is ISAC most likely to achieve large-scale deployment first in the near future? Vehicular networks, the low-altitude economy, industrial automation, smart cities, or other scenarios? Justify your answer from the four dimensions of spectrum efficiency, hardware cost, deployment efficiency, and business closed-loop capability.

    \item \textit{(Open Exploration)} This section emphasizes that the value of ISAC lies in the ``restructuring of system-level benefits.'' In practical commercialization, is it possible that some individual metric (for example, communication rate or sensing accuracy) may decrease slightly, while the overall system nevertheless becomes more valuable? Provide an example and discuss whether this would affect the industrial acceptance of ISAC.

\end{enumerate}

\noindent\textbf{Note:}
These exercises progress from conceptual understanding to comparative analysis,
in-depth discussion, and open exploration. Readers are encouraged to answer them
independently after studying this section. Some questions are also suitable for
classroom discussion, group seminars, or course assignments.