% chapters/chapter1/sec1.tex

\section{The Essence, Evolution, and Core Characteristics of Integrated Sensing and Communications}
\label{sec:ch1-essential-definition}

% TODO: This section is drafted by Huixin Man.
% Writing objectives:
% 1. Introduce the developmental background of wireless communication systems;
% 2. Motivate the 6G demand for the convergence of communications, sensing, and intelligence;
% 3. Explain the research significance of ISAC.

\subsection{Why Is It Necessary to Redefine Integrated Sensing and Communications}
\label{subsec:ch1-why-redefine-isac}
\subsubsection{The Long-Standing Separation Between Traditional Communication and Radar Systems}
\label{subsubsec:ch1-traditional-separation}

Wireless communication systems and radar systems are two fundamental branches of modern electromagnetic information technology. Although both rely on the transmission, propagation, and reception of radio-frequency signals, they were originally developed for different purposes and therefore evolved along largely independent technical paths.

The primary objective of a communication system is to enable reliable and efficient information transfer between a transmitter and a receiver. From the perspective of information theory, the Shannon capacity of an additive white Gaussian noise (AWGN) channel is given by \cite{Shannon1948}
\begin{equation}
C = B \log_2 \left( 1 + \frac{S}{N} \right),
\end{equation}
where $C$ denotes the channel capacity in bit/s, $B$ is the bandwidth in Hz, and $S$ and $N$ are the average signal and noise powers, respectively. This expression highlights the two central concerns of communication system design: maximizing transmission rate and ensuring reliable delivery. Accordingly, the evolution of communication systems has long focused on coding, modulation, multiple access, and resource allocation, while channel effects such as multipath fading and Doppler spread are typically treated as impairments to be mitigated \cite{Goldsmith2005,Andrews2014,TS38300}.

In contrast, the primary objective of a radar system is not information delivery, but environmental sensing through the analysis of reflected signals \cite{Skolnik2008,Richards2014}. Typical radar tasks include target detection, parameter estimation (e.g., range, velocity, and angle), target recognition, and high-resolution imaging. Detection is commonly formulated as a hypothesis testing problem, while estimation accuracy is often characterized by the Cramér--Rao lower bound (CRLB) \cite{Kay1993}. To support accurate sensing, radar waveform design typically aims at desirable ambiguity-function properties, such as a sharp mainlobe and low sidelobes in the delay--Doppler domain, so as to improve resolution and estimation performance \cite{Levanon2004,Richards2014}.

Therefore, although communication and radar systems share a common electromagnetic foundation, their fundamentally different design objectives have led to long-standing separation in spectrum usage, waveform design, hardware platforms, and receiver processing methods \cite{Liu2020JointRadarComm,Liu2022ISAC,Zhang2021ISAC6G}.

\begin{enumerate}[label=(\arabic*)]
    \item \textbf{Spectrum Usage}
    
    Traditionally, communication systems and radar systems have operated in separately allocated spectrum bands. Within the historical framework of spectrum regulation, the International Telecommunication Union (ITU) and the World Radiocommunication Conference (WRC) assign dedicated frequency bands to different services. For example, cellular communication systems mainly occupy bands from 700\,MHz to 3.5\,GHz, with 5G NR further extending into the millimeter-wave spectrum, whereas radar systems are commonly deployed in the S-, C-, and X-bands. Such spectral separation allows the two types of systems to operate independently with limited mutual interference.
    
    \item \textbf{Hardware Platforms}
    
    Communication and radar systems differ significantly in hardware architecture. Communication transceivers are typically optimized for the transmission and reception of linearly modulated signals, with emphasis on linearity and power efficiency. In contrast, radar systems, especially pulsed radars, often require high-power transmitters, low-noise receivers, and high-dynamic-range analog-to-digital converters (ADCs) to process weak echoes over a wide dynamic range. Their antenna designs also differ: radar systems often employ high-gain directional antennas or phased arrays, while communication base stations generally use omnidirectional or sectorized antennas to provide coverage.
    
    \item \textbf{Signal Design}
    \begin{sloppypar}
    Communication signals are primarily designed for information delivery. A representative example is the orthogonal frequency-division multiplexing (OFDM) waveform, whose design focuses on metrics such as spectral efficiency, peak-to-average power ratio (PAPR), and out-of-band emission \cite{Goldsmith2005,Andrews2014}. By contrast, radar waveforms are designed to optimize sensing performance. Classical radar signals, such as linear frequency-modulated (LFM) pulses and phase-coded waveforms, are typically designed based on ambiguity function characteristics to achieve high range and velocity resolution with low sidelobes \cite{Levanon2004}. Moreover, radar processing usually assumes that the transmitted waveform is known a priori, whereas communication signals may appear random from the radar perspective due to the unknown data symbols \cite{Liu2020JointRadarComm,Zhang2021ISAC6G}.
    \end{sloppypar}
    \item \textbf{Receiver Processing}
    
    The main task of a communication receiver is signal detection and data recovery, with typical procedures including synchronization, channel estimation, equalization, demodulation, and decoding \cite{Goldsmith2005}. In contrast, a radar receiver is concerned with target detection and parameter extraction, and its processing chain typically includes matched filtering, constant false alarm rate (CFAR) detection, Doppler processing, and angle estimation \cite{Skolnik2008,Richards2014}. In essence, communication receivers aim to recover transmitted information, whereas radar receivers aim to infer physical properties of the environment.
\end{enumerate}

\begin{longtable}{p{3.2cm}p{5.6cm}p{5.6cm}}
\caption{Core comparison between communication systems and radar/sensing systems}
\label{tab:comm-vs-radar}\\
\toprule
\textbf{Comparison Dimension} & \textbf{Communication Systems} & \textbf{Radar/Sensing Systems} \\
\midrule
\endfirsthead

\caption[]{Core comparison between communication systems and radar/sensing systems (continued)}\\
\toprule
\textbf{Comparison Dimension} & \textbf{Communication Systems} & \textbf{Radar/Sensing Systems} \\
\midrule
\endhead

\midrule
\multicolumn{3}{r}{\textit{Continued on next page}} \\
\endfoot

\bottomrule
\endlastfoot

\textbf{Core objective} 
& Reliable information transmission 
& Target detection and parameter estimation \\

\textbf{Spectrum usage} 
& Licensed communication bands 
& Dedicated radar bands \\

\textbf{Signal characteristics} 
& Random data-bearing modulation 
& Deterministic known waveform \\

\textbf{Role of the channel} 
& A ``pipe'' for information delivery, to be overcome 
& A ``carrier'' of sensing information, to be analyzed \\

\textbf{Transmit signal design criterion} 
& Spectral efficiency, bit error rate 
& Ambiguity function, resolution \\

\textbf{Receiver processing objective} 
& Bit recovery 
& Parameter extraction \\

\textbf{Performance metrics} 
& Capacity, throughput, latency 
& Detection probability, estimation accuracy \\

\textbf{Typical hardware architecture} 
& Base station/terminal 
& Radar station/sensor \\

\end{longtable}

Table~\ref{tab:comm-vs-radar} summarizes the main differences between conventional communication systems and radar sensing systems across multiple dimensions. In general, their separate evolution was historically reasonable in the pre-5G and early 5G eras. First, in the Sub-6 GHz range, the frequency bands used by communication and radar systems were largely separated, so spectrum conflicts were not yet prominent. Second, mobile networks at that stage mainly supported human-centric services such as voice and data transmission, with little need for explicit sensing or understanding of the physical environment. Third, both communication and radar had developed relatively mature and specialized technology stacks, making independent optimization within their respective domains an efficient approach.

However, this separated development paradigm is revealing increasingly significant limitations. First, spectrum scarcity has become more severe. As communication systems expand toward millimeter-wave (mmWave) and terahertz (THz) bands, their operating frequencies become increasingly adjacent to, or even overlap with, those of radar systems, placing growing pressure on conventional static spectrum allocation strategies \cite{TS38104,Zheng2019RadarCommunicationCoexistence}. Second, emerging applications such as autonomous driving, unmanned aerial vehicles, and smart cities require both communication and environmental sensing capabilities. In such scenarios, separate deployment of the two functions often leads to higher system complexity, cost, and latency \cite{Liu2022ISAC,De2021convergent}. Third, independent deployment results in increasing resource inefficiency, since communication base stations and radar platforms often have significant potential for sharing hardware resources such as RF front ends, antenna arrays, and signal processing units \cite{Liu2020JointRadarComm,Liu2022ISAC}.

These limitations together form the fundamental motivation for the development of integrated sensing and communications (ISAC) and provide the historical context for the growing need for communication-sensing convergence.

\subsubsection{Fundamental Demands for the Convergence of Communication and Sensing in Emerging Wireless Network Scenarios}
\label{subsubsec:ch1-fundamental demands}

The emergence of integrated sensing and communications (ISAC) is not merely the result of a new technical concept, but rather a response to the fundamental capability requirements imposed by emerging wireless network scenarios. Future wireless networks are expected to provide not only connectivity, but also environmental awareness and task-oriented support. In this context, communication systems are evolving from pure information delivery platforms into integrated information infrastructures with sensing, cognition, and decision-support capabilities \cite{Liu2022ISAC}.

First, spectrum scarcity and the inefficient duplication of resources by separate communication and sensing systems are major practical drivers for ISAC. Wireless communications and radar/sensing systems both rely on limited spectrum resources, while the demand for high-quality spectrum continues to grow with the rapid increase of mobile data traffic \cite{ITU_R_RR2024,miit_radio_freq_2026_en}. At the same time, mobile communication systems are expanding toward millimeter-wave and even terahertz bands, where coexistence and coordination with traditional radar, remote sensing, and radiolocation systems become increasingly challenging. Under such conditions, allocating dedicated spectrum resources separately to communication and sensing systems is becoming both difficult and inefficient. By enabling shared spectrum, shared infrastructure, and shared signal processing chains, ISAC offers a promising way to improve overall spectrum utilization. Moreover, if a unified waveform can simultaneously support data transmission and environmental sensing, the gain may go beyond simple resource sharing and lead to further improvements in spectral efficiency \cite{Liu2022ISAC,Hassanien2015dual}.

Second, there is a growing need to make sensing an intrinsic capability of network nodes such as terminals, base stations, and edge devices. In conventional systems, sensing is typically performed by dedicated hardware such as radar, cameras, or LiDAR, while communication networks mainly serve data delivery functions. However, many 6G-oriented application scenarios, including connected vehicles, autonomous driving, UAV networks, smart factories, industrial IoT, and smart cities, require network nodes not only to communicate, but also to perceive surrounding targets, environments, and system states in real time \cite{Zhang2021ISAC6G}. Embedding sensing functionality into communication systems can therefore reduce the reliance on standalone sensing devices while improving system integration, energy efficiency, and service capability.

More fundamentally, the necessity of ISAC stems from the changing role of wireless networks themselves. In 5G and earlier generations, wireless networks were mainly designed as information delivery pipelines, with primary emphasis on rate, latency, coverage, and connectivity. In contrast, the 6G vision views wireless networks as integrated platforms that jointly support communication, sensing, computing, and control \cite{Liu2022ISAC,Zhang2021ISAC6G}. This implies that future networks should not only transmit information, but also understand the physical environment, for example by sensing user locations, velocities, and activity states, characterizing surrounding objects, and exploiting the spatial structure of wireless channels. Such sensing information can further support intelligent network functions such as beam management, resource allocation, mobility management, and task coordination. For closed-loop applications such as autonomous driving, industrial automation, and remote operation, sensing is often the starting point for real-time decision-making and control. Therefore, sensing is becoming a native capability of future wireless networks rather than an optional add-on.

In this context, one may ask why an add-on solution consisting of a communication system plus a separate sensing system is not sufficient. Although such architectures are common in current engineering practice, their limitations become increasingly evident as future applications demand tighter real-time response, stronger coordination, lower cost, and larger deployment scale. Separate systems usually require additional interfaces, synchronization mechanisms, and information exchange procedures, which introduce non-negligible overhead and latency. Their independent design also makes it difficult to achieve globally efficient coordination in waveform design, resource allocation, protocol operation, and hardware implementation. In addition, deploying both communication and sensing hardware at every node leads to higher costs in hardware, energy consumption, installation, and maintenance. Data fusion between heterogeneous communication and sensing systems is also complex due to differences in timestamps, coordinate systems, data formats, and processing pipelines \cite{Liu2022ISAC,Hassanien2015dual}. By contrast, ISAC enables joint design at the levels of system architecture, signal design, resource scheduling, and receiver processing, thereby offering a unified technological path toward higher spectrum efficiency, stronger functional synergy, lower deployment cost, and better task support for future wireless networks.

\subsubsection{ISAC Cannot Be Simply Understood as a Combination of ``Communications + Radar''}
\label{subsubsec:ch1-isac-not-simple-combination}

After establishing the necessity of ISAC, it is important to clarify a common misconception: ISAC should not be understood as a simple combination of a communication system and a radar system. Existing studies have shown that the integration of communication and sensing can take place at different levels, ranging from physical co-location, hardware sharing, and spectrum coexistence to deep integration at the waveform, protocol, and network-architecture levels \cite{Liu2022ISAC,Zhang2021ISAC6G}. These approaches differ fundamentally in their degree of integration. Therefore, not every system in which communication and sensing coexist can be regarded as ISAC in the strict sense.

The most basic form is to deploy a communication device and a radar device at the same site, where the two systems operate independently and only share physical location. This arrangement is convenient for reusing infrastructure such as sites and power supply. However, communication and sensing remain separate in signal design, resource scheduling, and information processing. Hence, such a configuration should not be considered a truly integrated system.

A further step is to allow communication and sensing to share part of the hardware platform, such as the radio-frequency front-end, antenna array, or baseband processing unit, while performing the two functions separately through time switching, frequency switching, or mode switching. This approach can reduce cost, device size, and energy consumption, and it reflects a certain degree of coordination. Nevertheless, communication and sensing are still typically separated in an orthogonal manner, rather than operating simultaneously under a unified signal or resource-optimization framework. For this reason, it is more appropriate to view this type of system as a shared-platform implementation, or at most an elementary form of ISAC \cite{Hassanien2015dual}.

Another related concept is spectrum coexistence, in which communication systems and radar/sensing systems share the same spectrum and reduce mutual interference through methods such as dynamic allocation, interference suppression, or beam isolation \cite{Liu2020JointRadarComm}. The main concern in this line of research is compatibility and interference management, rather than unified functional design. As a result, communication and sensing in spectrum coexistence scenarios are still usually treated as two separate systems, which is fundamentally different from the deep integration pursued by ISAC \cite{Liu2022ISAC}.

In a stricter sense, genuine ISAC emphasizes deep coupling between communication and sensing across multiple layers. Its goal is not merely to avoid conflicts between the two functions, but to achieve synergistic gains through joint design \cite{Liu2022ISAC,Zhang2021ISAC6G}.Specifically, this deep integration is mainly reflected in the following aspects:

\begin{itemize}
    \item \textbf{Signal-level integration:} the same waveform simultaneously carries communication information and enables environmental sensing, rather than simply superimposing communication and sensing signals or alternating between them. Ideally, the communication data itself becomes part of the sensing waveform design, while the environmental information contained in sensing echoes can in turn support communication tasks such as link estimation, beam management, or channel prediction.

    \item \textbf{Resource-level integration:} wireless resources in the time, frequency, space, and power domains are jointly occupied by communication and sensing tasks and allocated under a unified optimization framework. Resource management is therefore no longer performed separately for ``the communication system'' and ``the sensing system,'' but must jointly consider tradeoffs among communication rate, latency, and reliability on the one hand, and sensing detection probability, estimation accuracy, and resolution on the other.
    
    \begin{sloppypar}
    \item \textbf{Hardware-level integration:} antenna arrays, RF chains, analog-to-digital/digital-to-analog converters, and baseband processing units are genuinely shared between communication and sensing functions, and the hardware architecture is designed from the outset to satisfy the requirements of both tasks, rather than merely running two independent software stacks on the same platform in alternation.
    \end{sloppypar}

    \item \textbf{Protocol-level integration:} air-interface protocols, frame structures, pilot and reference signal design, feedback mechanisms, random access procedures, and link maintenance processes must natively support sensing, rather than simply adding a sensing module on top of a conventional communication protocol. In other words, sensing should be incorporated into the protocol design from the beginning.

    \item \textbf{Network-level integration:} sensing must be incorporated into the overall network architecture, including sensing task triggering and scheduling, sensing data aggregation and distribution, multi-node cooperative sensing, and feedback from sensing results to network resource management. In this sense, sensing is no longer a local function of an individual node but part of a network-wide capability.

    \item \textbf{Service-level integration:} communication services and sensing services jointly support upper-layer applications, forming a complete service loop from environmental sensing to information transmission, then to computing, decision-making, and control execution. In scenarios such as autonomous driving, intelligent manufacturing, low-altitude coordination, and smart cities, this service-layer closed loop is one of the key manifestations of ISAC value.
\end{itemize}

\begin{sloppypar}
Therefore, the most fundamental distinction between ISAC and a traditional combined ``communication system + radar system'' solution does not lie in whether the two are installed at the same location or whether some hardware resources are shared. Rather, it lies in whether communication and sensing are jointly designed and jointly optimized across layers under a unified system objective. Only when communication and sensing are no longer treated as separate auxiliary functions, but instead become organically unified across waveforms, resources, protocols, networks, and service workflows, does a system truly exhibit the essential characteristics of ISAC. This multilayer, deeply coupled, task-oriented integration mechanism forms the central theme of the remainder of this book.
\end{sloppypar}

\subsection{The Basic Definition and Conceptual Boundaries of ISAC}
\label{subsec:ch1-basic-definition}
\subsubsection{The Definition of ISAC}
\label{subsubsec:ch1-definition-isac}

Having discussed the practical motivations behind ISAC, its core idea, and its distinction from concepts such as simple co-location or spectrum coexistence, we now proceed to provide a basic definition of ISAC and clarify its conceptual boundaries. It should be emphasized that although academia and industry still differ somewhat in their preferred implementation paths for ISAC, there is broad consensus on its essential meaning: the core of ISAC lies not in mechanically superimposing communication and sensing functions, but in achieving their joint design, coordinated operation, and bidirectional empowerment under a unified system objective \cite{Liu2022ISAC,Liu2020JointRadarComm}.

In this textbook, ISAC is defined as follows:
\begin{quote}
\textbf{ISAC (Integrated Sensing and Communications) refers to a class of technologies in which, under a unified system framework, communication and sensing functionalities are simultaneously enabled through shared or jointly designed signals, hardware, spectrum, air-interface mechanisms, and network mechanisms.}
\end{quote}

This definition contains several key elements, each of which deserves further explanation.
\begin{enumerate}[label=(\arabic*)]
    \item \textbf{A Unified System Framework}
    
    A primary feature of ISAC is \emph{unification}. Communication and sensing are not treated as two loosely coupled subsystems, but are modeled, designed, and operated within a common system framework \cite{Liu2022ISAC,Zhang2021ISAC6G}. Such unification may appear in the signal processing chain, wireless resource management, network architecture, and performance evaluation. Importantly, unification does not mean that communication and sensing have identical objectives. Instead, their different requirements, such as data rate, latency, detection probability, estimation accuracy, and resolution, are jointly considered and balanced within a single framework.
    
    \item \textbf{Resource Sharing and Coordinated Design}
    \begin{sloppypar}
    In ISAC systems, the integration of communication and sensing is typically realized through resource sharing or coordinated design, and practical systems often lie between these two extremes \cite{Liu2020JointRadarComm,Gonzalez2024integrated}. In the sharing mode, the two functions may use the same waveform, spectrum, hardware platform, or processing modules. In the coordinated design mode, even if they do not fully share the same resources, they are still jointly optimized in system design, for example in beamforming or power allocation. Therefore, ISAC is characterized more by the inherent coordination between communication and sensing than by complete resource sharing alone.
    \end{sloppypar}
    \item \textbf{Simultaneous Communication and Sensing Functions}
    
    The term ``simultaneous'' in ISAC should be understood from both the system objective and the operation mechanism \cite{Liu2022ISAC}. At the objective level, communication and sensing are both core functions from the outset, rather than one being subordinate to the other. At the operational level, they may be performed truly in parallel using the same signal or resource block, or executed in a quasi-simultaneous manner through rapid switching over a short timescale. Hence, the key criterion for identifying an ISAC system is not strict physical simultaneity, but whether the two functions are jointly designed and coordinately operated within a unified framework.
    
    \item \textbf{Broad Scope of Sensing Targets}
    
    In the ISAC context, sensing should be interpreted in a broad sense. Its targets extend far beyond the point targets typically considered in conventional radar systems \cite{Liu2022ISAC,Gonzalez2024integrated}. They may include the physical environment, moving objects such as vehicles and pedestrians, communication users, IoT devices, the electromagnetic propagation environment, and even vital signs or human activities. This broad sensing scope greatly expands the application boundary of ISAC and connects it closely with future wireless networks, ambient intelligence, and human--machine interaction.
    
    \item \textbf{Mutual Empowerment Between Communication and Sensing}
    
    Another essential characteristic of ISAC is the bidirectional relationship between communication and sensing \cite{Liu2022ISAC,Zhang2021ISAC6G}. On the one hand, sensing can assist communication by providing information such as user location, object motion, blockage conditions, and environmental structure, which is valuable for beam management, link establishment, channel prediction, and resource scheduling. On the other hand, communication systems provide signal sources, network coverage, synchronization mechanisms, distributed infrastructure, and feedback channels that naturally support sensing. Therefore, ISAC should not be viewed as simply adding sensing capability to a communication system, but rather as a unified framework in which the two functions enhance each other to improve overall system performance.
\end{enumerate}

Taken together, the basic definition of ISAC contains at least three core implications: first, communication and sensing are jointly designed and jointly operated at the system level; second, communication and sensing not only share resources, but can also create synergistic gains through joint optimization; and third, sensing in ISAC is broad, networked, and capable of feeding back to optimize communication performance. Understanding these key elements will help us more accurately grasp the research scope and technical boundaries of ISAC in subsequent discussions of signal models, system architectures, and performance tradeoffs \cite{Liu2022ISAC,Liu2020JointRadarComm,Gonzalez2024integrated}.

\subsubsection{Boundary Distinctions Between ISAC and Related Concepts}
\label{subsubsec:ch1-boundary-distinction}

In academic research, engineering practice, and standardization discussions surrounding ISAC, several closely related but non-equivalent technical concepts frequently appear. Accurately distinguishing the connections and differences between ISAC and these related concepts is important for building a clear technical picture, avoiding terminological confusion, and correctly understanding the actual scope of different research efforts. Broadly speaking, these related concepts may be grouped into three categories: first, the \emph{coexistence} problem, which focuses on interference management; second, \emph{joint radar--communication} or \emph{dual-function radar--communication} systems, which emphasize dual-functional waveforms and link-level co-design; and third, related terms such as Joint Communication and Sensing (JCAS), Joint Radar and Communication (JRC), and Radar--Communication (RadCom), which are close to ISAC in meaning but differ slightly in emphasis.

\paragraph{1) Difference between ISAC and Radar--Communication Coexistence}

\begin{sloppypar}
Radar--Communication Coexistence (RCC) is one of the earliest and most widely studied directions in the interaction between radar and communication systems. Its core question is the following: when communication and radar systems, originally designed independently, are forced to share the same or adjacent spectrum bands because of spectrum scarcity or deployment proximity, how can interference modeling, resource coordination, and signal processing be used to enable them to operate jointly with acceptable performance degradation \cite{Chiriyath2017RadarCommCoexistence,Liu2020JointRadarComm}. Typical research topics include analyzing and suppressing radar interference on communication receivers, evaluating the impact of communication signals on radar detection and parameter estimation, and designing coexistence strategies based on power control, beam nulling, cognitive spectrum access, frequency planning, and space--time interference suppression \cite{Deng2013InterferenceMitigation,Sodagari2012ProjectionBasedCoexistence,Zheng2019RadarCommunicationCoexistence}.
\end{sloppypar}

In essence, RCC deals with the \textbf{compatibility problem between two independent systems}. Under this framework, communication and radar systems each serve their own separate objectives, and their main relationship is to avoid damaging each other's operation or to coordinate under conflict. Thus, the starting point of coexistence research is conflict management, and its main goal is to reduce mutual interference so that both systems can function as normally as possible. By contrast, ISAC is concerned with \textbf{simultaneously realizing communication and sensing functionalities within a unified system framework}. Its goal is not merely to reduce friction between two systems, but to achieve joint design, coordinated optimization, and performance enhancement under a common system objective \cite{Liu2022ISAC}. In short, coexistence emphasizes ``how two systems can peacefully coexist,'' whereas ISAC emphasizes ``how one system can natively possess both capabilities.'' This distinction is the primary prerequisite for understanding the conceptual boundary of ISAC.

\paragraph{2) Relationship between ISAC and Dual-Function Radar--Communication / Joint Radar and Communication}

Dual-Function Radar--Communication (DFRC) systems are generally regarded as one of the most important technical origins of ISAC and one of the most representative branches of communication--sensing fusion research \cite{Hassanien2015dual,Liu2020JointRadarComm}. The core idea of DFRC is to design a dual-functional signal or transmission mechanism that can simultaneously support information transmission and target sensing, so that the same transmitted waveform can be demodulated by a communication receiver while also enabling a radar receiver to extract target range, velocity, angle, and other parameters from the echoes. Based on this idea, researchers have proposed many representative physical-layer methods, such as OFDM-based dual-function waveform design, joint beamforming, embedded information modulation, symbol-level waveform design, and Multiple-Input Multiple-Output (MIMO) radar--communication integrated architectures \cite{Hassanien2015dual,Zhang2021ISAC6G}.

Conceptually, DFRC may be understood as an important realization of ISAC.
At a technical level, it mainly concerns physical-layer signal design and
link-level transceiver design.
Many problems studied in DFRC, such as dual-functional waveform design,
joint transmission strategies, and communication--radar performance tradeoffs,
constitute key components of the ISAC technical framework.
However, the conceptual scope of ISAC is usually broader than that of DFRC
\cite{Liu2022ISAC,Gonzalez2024integrated}.
DFRC tends to focus more specifically on how a single signal or a single
transmission platform can simultaneously serve radar and communication purposes.
Its emphasis is mainly on the physical layer, waveform layer, array processing
layer, and link-level performance.
By contrast, ISAC not only includes these issues, but also emphasizes
higher-layer problems, such as network architecture, protocol mechanisms,
resource scheduling, multi-node cooperative sensing, sensing information
feedback and fusion, and service-loop construction.
Therefore, DFRC can be considered an important subset or implementation
direction of ISAC, but the two are not equivalent.
The former is more link-level and waveform-oriented, whereas the latter
represents a broader system-level framework.

It should further be noted that the term JRC overlaps substantially with DFRC in the literature, and both are often used to describe the joint design of radar and communication functions \cite{Liu2020JointRadarComm,Zhang2021ISAC6G}. In many cases, JRC emphasizes the idea of \emph{joint design}, whereas DFRC emphasizes the implementation feature that a single platform or waveform performs dual functions. However, this distinction is not absolute, and terminology varies across the literature. Therefore, when reading related work, one should interpret these terms in context rather than making rigid distinctions based solely on the literal wording.

\paragraph{3) Differences among ISAC, JCAS, JRC, RadCom, and related terms}
\begin{sloppypar}
In addition to DFRC, several other terms with meanings close to ISAC frequently appear in the literature, such as JCAS, JRC, and RadCom \cite{Liu2022ISAC,Gonzalez2024integrated}. These terms overlap to some degree, but they also reflect differences in research emphasis and disciplinary tradition.
\end{sloppypar}

Among them, JCAS is semantically the closest to ISAC, and in many papers the two are used almost interchangeably. Relatively speaking, JCAS emphasizes the word ``joint,'' highlighting the joint nature of communication and sensing design, whereas the word ``integrated'' in ISAC emphasizes deeper fusion at the levels of system architecture, resource management, protocol mechanisms, and service workflows. Thus, in terms of subtle semantic difference, ISAC typically implies stronger system-level integration than JCAS, although in practice the two often refer to closely related or overlapping research scopes.

JRC, by contrast, explicitly uses ``radar'' as the representative form of sensing, and is therefore more common in traditional radar--communication fusion research, especially when the main tasks involve radar detection, parameter estimation, and target tracking \cite{Liu2020JointRadarComm,Hassanien2015dual}. ISAC, by comparison, employs the broader term ``sensing,'' which may encompass not only radar targets in the conventional sense but also users, devices, environments, propagation structures, and even human activities. Therefore, JRC can often be regarded conceptually as a more specific, radar-oriented subset of ISAC.

RadCom or Radar--Communication is usually a broad field-level label that can refer in general to research on the integration of radar and communications, but its specific meaning depends heavily on context. In some papers it refers to coexistence problems, while in others it refers to joint design. Its definition is therefore not always used consistently. For this reason, using such terms in a textbook without explicit clarification may easily confuse beginners.

For the above reasons, this textbook consistently adopts ISAC as the core term. This choice is based on three main considerations. First, the word ``integrated'' better captures the deep coupling and holistic design of communication and sensing. Second, the word ``sensing'' is broader than ``radar'' and can cover radar detection, localization, environmental sensing, human activity recognition, and channel-environment sensing, among others. Third, ISAC has become one of the most widely used terms in academia and industry when discussing communication--sensing fusion, and has received sustained attention in 6G vision studies and related standardization discussions \cite{Liu2022ISAC,Gonzalez2024integrated,De2021convergent}.

\paragraph{4) The multilayer meaning of ``Integrated''}

Finally, it should be further emphasized that the word ``integrated'' in ISAC is not a one-dimensional concept, but rather a layered and systematic one. Integration does not simply mean that communication and sensing share a spectrum band or use a common hardware platform. Instead, it may appear across multiple layers ranging from the physical layer to the service layer \cite{Liu2022ISAC,Zhang2021ISAC6G,Liu2020JointRadarComm}. From the perspective of teaching and system analysis, this integration may be roughly summarized into the following levels:

\begin{itemize}
    \item \textbf{Signal-level integration:} communication and sensing use a unified waveform, or waveform design is jointly optimized to simultaneously support information transmission and parameter sensing.

    \item \textbf{Hardware-level integration:} antenna arrays, RF chains, ADCs/DACs, and baseband processing platforms are jointly used by communication and sensing, and the hardware architecture is designed to satisfy the requirements of both functions.

    \item \textbf{Algorithm-level integration:} signal processing and optimization algorithms simultaneously serve both communication and sensing objectives, such as joint channel estimation and target detection, joint beamforming, and joint resource scheduling with state sensing.

    \item \textbf{Network-level integration:} sensing is incorporated into the overall network architecture, including sensing task triggering and scheduling, sensing data uploading and distribution, multi-node cooperative sensing, and feedback from sensing results to communication network optimization.
    
    \begin{sloppypar}
    \item \textbf{Service-level integration:} communication and sensing services are jointly orchestrated for upper-layer tasks, forming a closed-loop service workflow of ``sensing--communication--computation--decision--control'' to support complex applications such as autonomous driving, industrial control, low-altitude coordination, and smart cities.
    \end{sloppypar}
\end{itemize}

It should be noted that different ISAC systems may exhibit different depths of integration across these levels. Therefore, ISAC in practice is not a binary concept of either integrated or not integrated, but is better understood as a continuous spectrum from shallow to deep fusion. For this reason, judging whether a system belongs to ISAC cannot be based simply on whether it shares part of the spectrum or hardware; rather, one should comprehensively evaluate the degree of integration and the depth of joint design across signals, resources, protocols, networks, and service workflows.

\subsubsection{The Working Definition of ISAC in This Textbook}
\label{subsubsec:ch1-working-definition}

After discussing the general definition of ISAC and its boundaries with related concepts, this textbook further introduces a \emph{working definition} of ISAC for teaching, modeling, and subsequent analysis. Such a working definition is necessary because ISAC is still a rapidly evolving research area, and its concrete realizations, system boundaries, and application emphases are not completely consistent across the literature. For a textbook, a general definition alone is insufficient; it is also necessary to explicitly state the basic standpoint, abstraction level, and analytical scope adopted throughout the book, so that the subsequent chapters can remain consistent in terms of theoretical models, system architectures, and performance metrics.

Based on this consideration, this textbook adopts the following interpretive framework for ISAC.
\begin{enumerate}[label=(\arabic*)]
    \item \textbf{ISAC is regarded as one of the key native capabilities of 6G and future wireless networks:}
    
    This textbook discusses ISAC within the broader technical framework of 6G and future wireless networks. Unlike traditional networks, which mainly emphasize connectivity, future wireless networks are widely expected to possess multiple capabilities simultaneously, including communication, sensing, computing, and control, with sensing no longer depending solely on external standalone sensor systems but gradually becoming one of the native capabilities of network nodes and infrastructure \cite{Liu2022ISAC,Gonzalez2024integrated,Saad2020Vision6G}. Under this positioning, the discussion of ISAC in this textbook is not limited to physical-layer signal design for point-to-point links, but also covers link-layer, network-layer, and system-level architectural issues, including cellular networking, multi-node cooperative sensing, edge computing support, and device--edge--cloud collaborative processing. In other words, the ISAC considered in this textbook is not merely a narrow ``dual-function waveform design problem,'' but a system-level capability framework for the evolution of future wireless networks.
    
    \item \textbf{The focus is on system-level problems of coordinated communication and sensing design:}
    
    The core concern of this textbook is not to discuss a single waveform, a single algorithm, or a single application in isolation, but to understand how communication and sensing functions can be jointly designed within a unified system so as to optimize overall performance and enhance task support capability \cite{Liu2020JointRadarComm,Zhang2021ISAC6G}. Specifically, the subsequent chapters will revolve around the following questions:
    \begin{itemize}
        \item How can signal models and transmit waveforms be designed to simultaneously support communication and sensing?
        \item How can wireless resources in time, frequency, space, and power be shared, allocated, and jointly optimized between communication and sensing?
        \item How can joint beamforming strategies be designed in MIMO, multi-antenna, and large-array systems to balance communication quality and sensing performance?
        \item How can a unified performance analysis framework be established to characterize the intrinsic tradeoffs among communication rate, bit error rate, latency, sensing detection probability, estimation accuracy, and resolution?
        \item How can network architectures support large-scale, multi-node, distributed, and cooperative ISAC services?
    \end{itemize}
    These questions correspond, respectively, to the signal layer, resource layer, array processing layer, performance evaluation layer, and network architecture layer in ISAC research, and together they form the main technical thread of this textbook.
    
    \item \textbf{No single optimal waveform, architecture, or application scenario is presupposed:}
    
    ISAC is an open and diverse technological framework, and there is no universally optimal waveform, universally optimal architecture, or single standard application paradigm \cite{Liu2022ISAC,Liu2020JointRadarComm}. Different frequency bands, node capabilities, network deployment modes, and service objectives all lead to substantially different ISAC system designs. Therefore, this textbook does not reduce ISAC to any fixed implementation, but instead introduces multiple representative technical pathways based on common principles, including but not limited to OFDM-based ISAC waveform design, MIMO-based joint beamforming schemes, sensing networking and cooperative processing in cellular systems, high-resolution sensing-and-communication systems in the mmWave/THz bands, and ISAC application frameworks for vehicular networks, the low-altitude economy, smart factories, and intelligent spaces \cite{Liu2022ISAC,Gonzalez2024integrated}. In this way, readers can understand both the common principles of ISAC and its differentiated implementation forms under different technical conditions and application scenarios.
\end{enumerate}

This working framework not only defines the scope of the textbook, but also lays the foundation for a unified mathematical modeling and performance analysis language in later chapters. Specifically, in the subsequent theoretical analyses of this book, communication performance will mainly be described by metrics such as channel capacity, achievable rate, bit error rate, reliability, and transmission latency; sensing performance will mainly be characterized by metrics such as detection probability, false alarm probability, range/velocity/angle resolution, estimation error, and the CRLB \cite{Liu2022ISAC,Zhang2021ISAC6G}. When communication and sensing need to operate jointly in a unified system, the two classes of metrics generally do not exhibit a simple monotonic relationship. Instead, their tradeoffs and synergy boundaries must often be characterized using tools such as multiobjective optimization, constrained optimization, and Pareto optimality \cite{Liu2020JointRadarComm}. In terms of system modeling, this textbook will strive to use a unified mathematical language to describe the transmit signal model, propagation channel model, target/scatterer model, observation model, and receiver processing chain, and on this basis gradually establish a joint performance evaluation framework for analyzing the relationships among rate, reliability, latency, localization accuracy, detection probability, estimation error, and energy consumption.

It should be emphasized that this working definition does not restrict ISAC to any narrow implementation. Rather, it means that in the subsequent chapters, any system that satisfies the following essential characteristic will be considered within the scope of ISAC: \emph{under a unified system framework, communication and sensing functions provide joint information transmission and environment/state sensing services through shared or jointly designed signals, resources, hardware, protocols, and network mechanisms, while exhibiting bidirectional empowerment between the two} \cite{Liu2022ISAC,Gonzalez2024integrated}. Conversely, schemes that only realize physical co-location, simple spectrum coexistence, or loose functional concatenation without a unified system objective and joint design mechanism will generally not be regarded in this textbook as part of the strict core category of ISAC.

Based on the above conventions, this textbook adopts the following working definition:
\begin{quote}
\textbf{ISAC is a key native capability for 6G and future wireless networks. It refers to the joint provisioning of information transmission and environment/state sensing services under a unified system framework through shared or jointly designed signals, resources, hardware, protocols, and network mechanisms, while supporting network intelligence, scene understanding, and service loops through the bidirectional empowerment of communication and sensing.}
\end{quote}

This working definition will serve as the common starting point for the system modeling, algorithm design, performance analysis, and application discussions throughout the subsequent chapters of this book.

\subsection{The Three-Stage Logic of ISAC Evolution}
\label{subsec:ch1-evolution-logic}

The development of ISAC technology did not occur overnight. Rather, it has undergone a gradual evolution from a state in which communication and sensing were independent but forced to coexist, to one in which they are deeply integrated under a unified system framework. To help readers understand this developmental trajectory, this textbook summarizes the evolution of communication--sensing fusion into three stages with clear progressive relationships: the \emph{spectrum coexistence and cross-application stage}, the \emph{dual-functional platform and joint signal design stage}, and the \emph{6G-oriented native integrated sensing and communication stage}. These three stages should not be understood as strictly isolated historical episodes, but rather as a technological spectrum in which the focus of research deepens and the degree of system integration continuously increases. Understanding the core objectives, representative solutions, and inherent limitations of each stage helps reveal the internal logic by which ISAC evolved from ``coexistence'' to ``integration.''

\subsubsection{Stage 1: Spectrum Coexistence and Cross-Application Phase}
\label{subsubsec:ch1-stage1}

The first stage in the evolution toward ISAC may be summarized as the \emph{spectrum coexistence and cross-application phase}. This stage roughly originated when communication systems and radar systems began to experience significant spectrum conflicts. The core question in this phase was not ``how to build one system that performs both communication and sensing,'' but rather ``when two originally independent systems must share the same spectrum or occupy adjacent bands, how can mutual interference be minimized so that both systems can continue to function properly?'' \cite{Liu2020JointRadarComm,Chiriyath2017RadarCommCoexistence}. Hence, the defining characteristic of this stage is that communication and radar systems remain independent in terms of objectives, architectures, waveforms, protocols, and performance evaluation, while some degree of coordination and compatibility is needed at the spectrum level.

From a system perspective, the central contradiction in this stage arises from the tension between spectrum scarcity and the independent deployment of two separate systems. Communication and radar each use their own signal formats, hardware platforms, receiver processing chains, and optimization objectives: the former usually aims for higher transmission rate, lower bit error rate, and better link reliability, whereas the latter focuses on detection probability, false alarm probability, parameter estimation accuracy, and spatial resolution. Under such circumstances, research and engineering practice were mainly concerned with building \emph{compatibility mechanisms}, rather than building a unified system \cite{ITU_R_RR2024}. In other words, the ``jointness'' at this stage exists only in spectrum coordination, not yet in integrated signal design, resource optimization, or network architecture.

Typical research problems in this stage include the following:
\begin{itemize}
    \item \textbf{Spectrum conflict analysis:} quantitatively evaluating the mutual impact between communication and radar systems under co-channel or adjacent-channel operation, including statistical modeling of interference signals, interference power calculation, received SINR analysis, and evaluation of the effects of interference on communication bit error rate, radar detection performance, and parameter estimation accuracy \cite{Chiriyath2017RadarCommCoexistence}.
    
    \item \textbf{Interference management:} designing mechanisms to reduce mutual interference, such as transmit power control, directional beam isolation, guard band design, dynamic spectrum coordination, space--time filtering, and interference cancellation at the receiver \cite{Liu2020JointRadarComm}.
    
    \item \textbf{Coexistence mechanism design:} establishing operating rules for communication and radar systems under shared spectrum, including sensing- and cognition-based dynamic spectrum access protocols, spectrum occupancy detection, shared timing coordination, and spectrum reuse strategies that satisfy regulatory requirements \cite{Chiriyath2017RadarCommCoexistence}.
\end{itemize}

In essence, during the coexistence stage, communication and radar still follow the philosophy of ``independent optimization with compatible operation.'' Communication systems are designed around transmission efficiency and link quality, whereas radar systems are designed around detection and estimation performance. There is no true unified objective function between them, nor is there a joint optimization mechanism spanning transmission, reception, resource scheduling, and protocol control. Thus, the technical boundary of this stage can be summarized as follows: \textbf{coordination exists at the level of interference management, but true integration at the level of system design is absent}. This is also the fundamental difference between this stage and the later stages of ISAC.

Several representative technical solutions appeared in this coexistence stage. Although they did not yet achieve integrated design, they laid the problem and methodological foundations for later deep fusion of communication and sensing.
\begin{itemize}
    \item \textbf{Time-division sharing:} communication and radar systems alternately use the same frequency band in the time domain, for example by scheduling communication transmission during radar pulse intervals or assigning predefined time slots separately to sensing and communication tasks. This approach is relatively simple to implement, offers strong isolation between systems, and is convenient for regulatory compliance and deployment. However, its drawback is that the spectrum cannot be truly used simultaneously, and the improvement in overall spectral efficiency is limited \cite{Chiriyath2017RadarCommCoexistence}.
    
    \item \textbf{Frequency-division isolation:} within a shared or adjacent spectrum range, communication and radar are allocated different subbands, and adjacent-channel interference is reduced through guard bands, filtering, and frequency planning. This approach is straightforward in engineering practice and is compatible with existing spectrum management frameworks. However, it is still essentially resource partitioning rather than functional integration, and therefore cannot fully exploit the potential of wideband spectrum resources \cite{ITU_R_RR2024}.
    
    \item \textbf{Coexistence-aware sensing or communication processing:} the receiver or signal processing stage explicitly takes into account the interference structure generated by the other system. For example, a radar receiver may model communication signals as structured interference and suppress them, or a communication receiver may detect, estimate, and cancel radar pulse interference. Such methods improve coexistence capability without changing the independence of the two systems \cite{Chiriyath2017RadarCommCoexistence,Liu2020JointRadarComm}.
    
    \item \textbf{Opportunistic spectrum reuse:} inspired by cognitive radio, the system performs spectrum sensing, occupancy detection, or environmental cognition to determine whether a frequency band is idle or under low interference, and then opportunistically reuses that band under certain constraints. In theory, this approach can improve spectrum utilization, but it places stringent requirements on sensing accuracy, fast access mechanisms, and regulatory compatibility \cite{Chiriyath2017RadarCommCoexistence,Haykin2005CognitiveRadio}.
\end{itemize}

Although these coexistence solutions alleviate spectrum conflict to some extent, their limitations are also evident. First, under the coexistence framework, improving the performance of one system often comes at the expense of degrading the performance of the other, leaving limited room for overall performance improvement. Second, since communication and radar systems remain independent in terms of hardware, waveforms, protocols, and information processing chains, they are unable to form a unified architecture or realize deep resource sharing. Third, the lack of substantive bidirectional information exchange and joint optimization prevents the release of the potential synergistic gains of sensing-assisted communication and communication-empowered sensing. Finally, from the engineering perspective, maintaining two separate systems together with their coordination mechanisms also introduces additional complexity and deployment cost \cite{Liu2020JointRadarComm,Liu2022ISAC}. These inherent limitations drove research beyond the question of ``how to coexist'' toward the question of ``how to realize dual functionality on the same platform and within the same signal,'' thereby leading to the second stage of ISAC evolution.

\subsubsection{Stage 2: Dual-Functional Platform and Joint Signal Design Phase}
\label{subsubsec:ch1-stage2}

If the keyword of the first stage is ``coexistence,'' then the keyword of the second stage is ``joint design.'' This stage marks the first substantial leap from compatibility between two independent systems to the realization of dual functionality on the same platform or within the same signal. It therefore constitutes the first real transition from coexistence to integration in the evolution toward ISAC. The most representative idea of this stage can be summarized as ``one signal, dual purposes'' or ``one platform, dual functions'': communication and sensing no longer rely on two separate transmitters, receivers, and waveform systems, but begin to share the same transmit waveform, antenna array, RF front end, and even parts of the receiver processing chain.

From the perspective of technical objectives, the core issue of this stage is no longer simply reducing interference between two systems, but rather how to jointly design a single signal or platform so that it simultaneously satisfies the performance requirements of both communication and sensing. It is in this stage that DFRC, JRC, and early physical-layer ISAC methods gradually developed into a relatively complete technical framework \cite{Liu2020JointRadarComm,Zhang2021ISAC6G,Hassanien2015dual}. Representative research directions in this stage mainly include the following:
\begin{itemize}
    \item \textbf{Dual-function waveform design:} how to design a transmit waveform that is simultaneously suitable for data transmission and target sensing, so that it has sufficient information-carrying capability while also exhibiting proper time--frequency characteristics for target detection, parameter estimation, and range--velocity resolution \cite{Liu2020JointRadarComm,Hassanien2015dual}. The essential challenge here is that communication and sensing often impose different waveform requirements: communication prefers strong modulation flexibility, high spectral efficiency, and robustness against multipath, whereas sensing is more concerned with autocorrelation properties, ambiguity function shape, bandwidth utilization, and target parameter identifiability. Thus, dual-function waveform design is fundamentally a joint optimization problem seeking a balance between communication achievable rate and sensing estimation performance.
    
    \item \textbf{Joint beamforming:} in multi-antenna and MIMO systems, how to design the transmit precoding matrix or beamforming vector so that it can simultaneously provide communication users with sufficient Signal-to-Interference-plus-Noise Ratio (SINR) or rate guarantees while also forming the desired illumination power, spatial focusing capability, or angular resolution in the target direction \cite{Liu2020JointRadarComm,Liu2022ISAC}. This problem is inherently multiobjective, because communication beams often favor user directions, whereas sensing beams may need to cover target regions or create specific beampattern structures, leading to conflicts in the allocation of spatial resources.
    
    \item \textbf{Shared resource scheduling and joint optimization:} when communication and sensing share the same set of time, frequency, space, and power resources, how to optimally allocate these resources under system constraints becomes another core issue of this stage \cite{Zhang2021ISAC6G,Liu2022ISAC}. Such problems may arise in frame-level pilot/data/sensing allocation, subcarrier selection, power loading, array degree-of-freedom allocation, and time-slot structure configuration. In essence, these problems require a unified framework for analyzing tradeoffs between communication and sensing performance metrics.
\end{itemize}

Although the second stage already achieved substantial joint design of communication and sensing at the physical and link layers, its research boundary was still largely limited to single-link, single-node, or single-cell scenarios. Specifically, joint waveform design was usually studied for point-to-point or point-to-multipoint links, joint beamforming was mostly analyzed within a single base station or transmission platform, and performance evaluation was mainly based on link-level theoretical analysis or simulation \cite{Liu2020JointRadarComm,Liu2022ISAC}. By contrast, issues such as multicell cooperative sensing, network-level sensing task scheduling, sensing result aggregation and fusion, end-to-end orchestration of sensing services, and sensing--edge-computing collaboration had not yet become the main focus of this stage. Therefore, from the perspective of technical evolution, although the second stage laid the core theoretical foundations of ISAC, its system perspective remained primarily link-level and platform-level rather than network-native.

In terms of implementation, several representative types of solutions emerged in this stage. These solutions constitute the most important technical foundation for later ISAC research.
\begin{itemize}
    \item \textbf{OFDM-based ISAC schemes:} OFDM is one of the most representative dual-functional signal carriers in this stage because it naturally possesses a regular time--frequency structure, mature communication transceiver mechanisms, and convenient processing properties for parameter estimation \cite{Liu2022ISAC,Sturm2011WaveformDesign,Zhou2022integrated}. In such schemes, the OFDM waveform carries communication data while target range and velocity are extracted from the received echoes through joint processing across the subcarrier and symbol dimensions. Since the two-dimensional time--frequency structure of OFDM corresponds naturally to the range--Doppler processing in radar, many methods can achieve efficient parameter estimation using Two-Dimensional Fast Fourier Transform (2D-FFT) or its variants. The significance of these schemes lies in the direct demonstration that mainstream communication waveforms can support basic sensing tasks with relatively minor modifications, thereby strongly promoting the evolution of communication systems into ISAC platforms.
    
    \item \textbf{DFRC waveform design:} another important technical route is to embed communication information into traditional radar waveforms, or to explicitly impose radar-oriented structural constraints on communication signals, thereby forming truly dual-functional waveforms \cite{Hassanien2015dual,Blunt2016overview,Blunt2010Embedding}. Such methods include, but are not limited to, embedding modulation information into pulse radar or LFM signals, realizing spatial modulation by antenna indexing or beam switching, optimizing the ambiguity function of the transmit waveform under communication quality constraints, and jointly designing information embedding mechanisms within MIMO radar waveforms. Compared with directly reusing existing communication waveforms, DFRC methods often emphasize constructing the dual-functional signal from the radar-performance perspective, which can offer advantages in target detection and angle control, but may face challenges in communication compatibility, standards adaptation, and system complexity.
    
    \item \textbf{MIMO joint design and beamforming:} with the development of multi-antenna technology, MIMO became one of the most important platforms for joint design in this stage \cite{Liu2020JointRadarComm,Li2023integrated}. In such schemes, the transmitter jointly designs the precoding matrix, covariance matrix, or beamforming vector so that user SINR, rate, or bit error rate constraints are simultaneously satisfied together with the sensing-side requirements on beampattern shape, illumination power, and angular discriminability. These problems are often formulated as multiobjective optimization, constrained optimization, or robust optimization problems, and are commonly solved using Semidefinite Relaxation, Alternating Optimization (AO), weighted-sum methods, penalty methods, and block coordinate descent. The importance of MIMO joint design lies in the fact that it translates the conflict and synergy between communication and sensing into a unified optimization framework, thereby laying the methodological foundation for later developments in massive MIMO, mmWave beam management, and network-level cooperative sensing.
   
    \begin{sloppypar}
    \item \textbf{Joint performance optimization for link-level tradeoffs:} beyond specific waveform and array designs, the second stage also gradually established the theme of \emph{communication--sensing performance tradeoff} as a central research topic \cite{Liu2020JointRadarComm,Liu2022ISAC}. Representative works include deriving tradeoff relationships between communication rate and detection performance, characterizing constraint relationships between bit error rate and radar parameter estimation accuracy, and analyzing the achievable performance region of dual-function systems through Pareto boundaries, multiobjective optimization, and constrained optimization. It is within this class of studies that ISAC began to form its own distinctive language and methodology of performance analysis.
    \end{sloppypar}
\end{itemize}

Overall, the significance of the second stage is that it systematically demonstrated, for the first time at the physical and link layers, that communication and sensing need not merely coexist, but can be genuinely fused on the same signal, the same platform, and within the same optimization framework \cite{Liu2020JointRadarComm,Liu2022ISAC,Hassanien2015dual}. Through this stage, researchers gradually developed a set of core theories, mathematical models, and algorithmic tools centered on dual-functional waveforms, joint beamforming, joint resource optimization, and communication--sensing performance tradeoffs, and verified the feasibility and effectiveness of mainstream communication technologies such as OFDM and MIMO as carriers of ISAC. However, this stage remained mainly focused on link-level and platform-level problems, with limited attention to network-level cooperation, service-oriented sensing, and native architectural support. Therefore, with the emergence of the 6G vision and the demand for network intelligence, ISAC naturally evolved toward the third stage, namely the stage of native integrated sensing and communication as a built-in network capability.

\subsubsection{Stage 3: 6G Native Integrated Sensing and Communication Phase}
\label{subsubsec:ch1-stage3}

The third stage represents the frontier direction of ISAC development and is widely regarded as an important vision for 6G wireless networks \cite{Liu2022ISAC,Gonzalez2024integrated,Saad2020Vision6G}. The most fundamental characteristic of this stage is that sensing is no longer treated as an external add-on to communication systems, but is elevated to a \emph{native capability} of wireless networks. The term ``native'' means that sensing is incorporated into the overall network design from the outset and is natively supported at multiple levels, including standards and protocols, network architecture, resource scheduling, service orchestration, and end-to-end application support. Compared with the first two stages, ISAC in this stage no longer remains mainly at the level of physical-layer waveform design and link-level optimization, but expands into a system-level design problem covering the physical layer, link layer, network layer, and even the application and service layers \cite{Liu2022ISAC,Zhang2020perceptive}.

From the technical standpoint, the essence of this evolution is the expansion of the ISAC research object from a \emph{single-link dual-functional platform} to a \emph{networked, service-oriented, and intelligent communication--sensing system}. In other words, while the second stage asks ``how can one platform communicate and sense simultaneously?'' the third stage further asks ``how can one network natively possess sensing capability and provide it as a service to support complex applications?'' \cite{Zhang2020perceptive,Cui2024integrated}. Under this view, the integration boundary between communication and sensing is significantly broadened, and network-level cooperation, computing collaboration, service loops, and intelligent control become essential parts of ISAC.

Representative technical problems in the third stage include the following:
\begin{itemize}
    \item \textbf{Network-level cooperative sensing:} how can observation resources from multiple base stations, access points, or sensing nodes in a cellular network be coordinated to achieve wider-area, more robust, and higher-resolution cooperative sensing \cite{Zhang2020perceptive,Cui2024integrated}? In this context, issues such as inter-node time synchronization, frequency synchronization, phase consistency, observation data feedback, distributed fusion, and joint target tracking all significantly affect system performance.
    
    \item \textbf{Cellular ISAC networking:} how can sensing functionality be deployed and managed within a cellular network topology so that sensing coverage and sensing resolution can be coordinated with communication coverage, user capacity, and interference management \cite{Liu2022ISAC,Zhang2020perceptive}? This involves many aspects, including the relationship between sensing cells and communication cells, sensing task triggering mechanisms, air-interface resource allocation, and functional splitting at the radio access network side.
    
    \item \textbf{Device--edge--cloud collaborative processing:} because raw sensing data are often large in scale and require timely processing, how to distribute sensing data processing, compression, fusion, and decision tasks among devices, edge nodes, and cloud platforms becomes an important system-level problem in this stage \cite{Gonzalez2024integrated,Saad2020Vision6G}. This issue affects not only sensing accuracy but also backhaul load, system latency, and energy consumption.
    
    \item \textbf{Service-loop support:} how to feed sensing results back in real time to communication, computing, and control systems so as to form a closed-loop service chain of ``sensing--transmission--computation--decision--control'' is one of the key features distinguishing this stage from the previous two \cite{Liu2022ISAC,Saad2020Vision6G}. In scenarios such as autonomous driving, industrial control, unmanned system collaboration, and digital twins, sensing is no longer merely an independent output, but the initial step and critical input of the entire task loop.
\end{itemize}

\begin{sloppypar}
Compared with the previous two stages, the technical boundary of the third stage has clearly expanded from link-level fusion to system-level, network-level, and service-level fusion. Specifically, the design object of ISAC is no longer confined to a single base station, a single platform, or a single link, but extends to the joint optimization of the entire network system. This expansion manifests itself at least in three respects \cite{Zhang2020perceptive,Cui2024integrated}. First, at the resource management level, sensing resource scheduling, multicell interference and coordination, sensing coverage planning, and cross-node observation cooperation must all be handled at the network-wide scale. Second, at the architecture and protocol levels, sensing must be incorporated into network functional entities and control-plane design, for example by introducing sensing task management, sensing data fusion and analysis, and service orchestration modules at the core network or edge side, while natively supporting sensing signal transmission, observation, and feedback at the air interface and control protocols of the access network. Third, at the service level, communication services and sensing services no longer run along two independent pipelines, but are jointly orchestrated and delivered for upper-layer tasks, allowing applications to request combined ``connectivity + sensing + computing'' capabilities on demand.
\end{sloppypar}

At this stage, ISAC systems begin to exhibit new capabilities and system-level value that were difficult to achieve in the first two stages.
\begin{itemize}
    \item \textbf{Sensing-assisted communication:} sensing results are used in reverse to improve communication performance. For example, by obtaining user location, movement trajectories, environmental blockage states, and spatial propagation structures, the network can perform beam prediction, handover preparation, blockage warning, and resource scheduling in advance, thereby reducing beam training overhead, improving link stability, and lowering handover latency \cite{Liu2022ISAC,Zhang2020perceptive}. This capability is particularly important in the mmWave and THz bands, where narrow-beam high-frequency communication is highly sensitive to spatial state information.
    
    \item \textbf{Communication-empowered sensing:} the existing infrastructure, signal resources, and spatiotemporal coverage of communication networks are used to realize large-scale and continuous environmental sensing \cite{Liu2022ISAC,Gonzalez2024integrated}. For example, the multi-base-station deployment of cellular networks naturally provides a distributed observation network for cooperative sensing, continuously available downlink and uplink communication signals can serve as opportunistic illumination sources, and network synchronization and backhaul mechanisms provide the basis for multi-node data fusion. Compared with traditional standalone sensing systems, this approach is more conducive to wide-area coverage and infrastructure reuse.
    
    \item \textbf{Sensing-driven network intelligence:} physical-world information obtained from sensing is incorporated into intelligent network decision-making, such that resource scheduling, mobility management, load balancing, beam control, and quality-of-service assurance no longer rely solely on communication-side feedback, but can instead be optimized based on real-time understanding of the physical environment \cite{Saad2020Vision6G,Cui2024integrated}. This also creates a much tighter coupling between Artificial Intelligence / Machine Learning (AI/ML) techniques and ISAC, pushing the network from an ``adaptive connectivity system'' toward an ``intelligent system with environmental awareness.''
    \begin{sloppypar}
    \item \textbf{Service loop:} a complete closed loop of ``sensing--communication--computation--decision--control--re-sensing'' is formed \cite{Saad2020Vision6G,Liu2022ISAC}. For instance, in industrial automation, when the network-side sensing system detects abnormal equipment operation, the observed information can be quickly transmitted to an edge computing node through the communication link, where condition assessment and control decisions are made; the control commands are then delivered to the actuators, and the sensing function continues to monitor the outcome and provide feedback. Such a closed-loop capability means that ISAC is no longer merely a functional extension of communication systems, but becomes an important foundational capability for digitalized, intelligent, and automated applications.
    \end{sloppypar}
\end{itemize}

From the perspective of technological evolution, the third stage marks a fundamental transition of ISAC from a \emph{link-level dual-functional technology module} to a \emph{network-level native capability framework} \cite{Liu2022ISAC,Zhang2020perceptive,Cui2024integrated}. In this stage, ISAC is no longer merely a signal processing problem in physical-layer research, but also becomes a topic of common concern in network architecture design, protocol evolution, edge intelligence, standardization, and industrial ecosystem development. At the same time, this stage raises many open questions that still require in-depth study, such as the fundamental performance limits of network-level ISAC, optimal task allocation mechanisms for multi-node cooperative sensing, security and privacy protection of sensing data, and business models and resource pricing methods for sensing-as-a-service \cite{Gonzalez2024integrated,Cui2024integrated}.

From the standpoint of standardization and industrial evolution, ISAC is also moving gradually from academic research toward engineering system construction. In recent years, the Third Generation Partnership Project (3GPP) has launched discussions on ISAC-related capabilities and initiated related study work in Release 19. At the same time, in International Mobile Telecommunications 2030 (IMT-2030)-oriented 6G vision studies, the integration of sensing and communications has already been identified as an important direction for future wireless networks \cite{IMT2030Framework,ThreeGPPRel19ISAC}. These developments indicate that the third stage is not merely an abstract vision, but is progressively entering a phase where it can be researched, implemented, and promoted through standardization.

\subsection{The Core Driving Forces Behind the Three-Stage Evolution}
\label{subsec:ch1-evolution-driving-force}

The evolution of ISAC along the three stages described above is not the result of several isolated technical solutions being accidentally assembled together. Rather, it has been jointly driven by a series of long-standing and increasingly strong structural forces. These driving forces include objective constraints at the spectrum and hardware-resource levels, as well as capability demands imposed by future network positioning, emerging application scenarios, and the trend toward intelligent systems. Understanding these drivers helps reveal, at a deeper level, the internal logic by which ISAC evolved from coexistence to integration, and further from link-level integration to a network-level native capability.

\subsubsection{Spectral Efficiency and Resource Reuse Requirements}
\label{subsubsec:ch1-driving-force-spectrum}

Spectrum scarcity is one of the most direct drivers of ISAC development. As global mobile data traffic continues to increase, the demand for wireless spectrum keeps rising, while high-quality contiguous spectrum suitable for mobile communications, especially in the sub-6 GHz range, has become increasingly scarce \cite{ITU_R_RR2024,miit_radio_freq_2026_en,Saad2020Vision6G}. At the same time, in order to support higher throughput and larger system capacity, communication systems are moving toward the mmWave and even THz bands, where there is growing overlap or adjacency with the operating frequencies of radar, remote sensing, and radiolocation systems \cite{Liu2022ISAC}. It is under this background that spectrum conflict between communication and sensing first drove the development of spectrum coexistence and interference management technologies in the first stage.

However, coexistence can only alleviate conflict to a limited degree and cannot fundamentally improve spectrum utilization efficiency. The basic reason is that, under the coexistence framework, communication and sensing systems still remain competitors in essence: improving the performance of one system often compresses the usable resources or raises the interference level for the other \cite{Liu2020JointRadarComm,Chiriyath2017RadarCommCoexistence}. For this reason, simple coexistence mechanisms cannot fully exploit the potential of shared spectrum. By contrast, if communication and sensing can share the same transmit signal, the same time--frequency resources, and even the same hardware platform, then the same physical resources can simultaneously serve the dual purposes of information transmission and environmental sensing, yielding resource reuse gains beyond those achievable by simple time-sharing or frequency-sharing. This transition from ``spectrum sharing'' to ``signal and function sharing'' constitutes one of the most fundamental motivations for the joint signal design of the second stage \cite{Liu2022ISAC,Hassanien2015dual}.

At a deeper level, as 6G networks are expected to simultaneously support communication, sensing, localization, computing, and control, the traditional system design paradigm of ``one function occupying one dedicated set of resources'' is becoming unsustainable \cite{Gonzalez2024integrated,Saad2020Vision6G}. Future networks must allow time, frequency, space, and power resources to support multiple functions at once. This means that system design philosophy must evolve from ``function-specific resource allocation'' toward ``resource reuse, functional coordination, and unified scheduling.'' ISAC is precisely the representative manifestation of this trend in the wireless air interface and network architecture.

\subsubsection{Hardware Integration and the Development of Reconfigurable Platforms}
\label{subsubsec:ch1-driving-force-hardware}

If spectrum pressure provides the external impetus for ISAC, then advances in hardware platforms provide the key physical foundation for its realization. One major reason why communication and sensing have gradually moved from being merely combinable in theory to being implementable in practice is that modern wireless hardware platforms are becoming increasingly reconfigurable, broadband, array-based, and software programmable.

First, the development of Software-Defined Radio (SDR) and general-purpose baseband platforms has made it possible for the same RF and baseband hardware to support different signal schemes and processing chains through software configuration, thereby significantly lowering the barrier to implementing communication and sensing on the same platform \cite{Mitola1995SDR}. This programmability means that it is no longer necessary to deploy completely separate hardware chains for different functions. Instead, multitask reuse can be achieved through software upgrades, parameter reconfiguration, and functional switching. This provides the essential foundation for dual-functional platform design in the second stage.

Second, the development of massive MIMO and phased-array technologies has provided ISAC with abundant spatial degrees of freedom. By configuring a large number of antenna elements, the system can simultaneously form multiple beams with different directions, widths, and power distributions in the spatial domain. This allows high-quality directional coverage for communication users while also providing controllable illumination and angular resolution for sensing targets \cite{Liu2020JointRadarComm,Li2023integrated}. It is precisely this spatial flexibility that makes joint beamforming and spatial resource reuse possible, and that gives practical feasibility to many of the MIMO-based joint design schemes in the second stage.

Third, mmWave and THz communication technologies naturally exhibit physical properties that are highly compatible with sensing requirements. High-frequency systems usually have much larger available bandwidth, which enables higher range resolution. In the classical monostatic setting, for example, the range resolution approximately satisfies
\[
\Delta R = \frac{c}{2B},
\]
where $c$ denotes the speed of light (m/s) and $B$ is the effective signal bandwidth (Hz) \cite{SkolnikRadarBook}. This means that a larger bandwidth yields stronger resolvability between targets in the range dimension. At the same time, mmWave and THz systems usually rely on large antenna arrays and narrow-beam transmission, which are naturally beneficial for improving angular resolution and spatial focusing capability \cite{Rappaport2019WirelessTHz}. Therefore, from the perspective of physical-layer characteristics, high-frequency communication systems inherently possess the potential to perform high-precision sensing tasks. This is also one of the main reasons why ISAC has attracted particular attention in the mmWave and THz bands.

It should also be noted that at lower frequencies, traditional communication equipment and radar equipment often differ significantly in RF architecture, bandwidth requirement, and array structure, making hardware sharing relatively difficult. By contrast, in the mmWave and higher-frequency ranges, communication and sensing systems exhibit increasing convergence in front-end implementation, as both tend to rely on broadband RF chains, phased-array structures, high-speed ADC/DAC modules, and tightly coupled digital beamforming architectures \cite{Liu2022ISAC,Rappaport2019WirelessTHz}. This hardware convergence substantially lowers the engineering barrier to realizing communication and sensing on a common platform, thus pushing ISAC from a conceptually feasible idea toward a practically realizable system.

In addition, the development of new reconfigurable electromagnetic devices has opened up new design space for ISAC. Reconfigurable Intelligent Surfaces (RIS), as a representative example of programmable electromagnetic environment technology, can actively shape the wireless propagation environment by adjusting the amplitude and phase responses of reflecting elements, thereby simultaneously serving communication link enhancement and sensing coverage extension \cite{Chepuri2023integrated}. In ISAC scenarios, RIS can not only improve coverage blind spots, enhance sensing echoes, or create favorable propagation paths, but also provide additional degrees of freedom for the joint optimization of communication and sensing. For this reason, RIS has become one of the important recent research hotspots.

\subsubsection{Network Intelligence and Service-Loop Requirements}
\label{subsubsec:ch1-driving-force-network}

Beyond the driving forces arising from resource and hardware constraints, the changing role of mobile communication networks themselves is also an important factor in the evolution of ISAC. In 5G and earlier generations, the main value of wireless networks lay in providing high-quality connectivity. In the 6G vision, however, networks are expected to evolve further into comprehensive service platforms that integrate connectivity, sensing, computing, control, and intelligence \cite{Gonzalez2024integrated,Saad2020Vision6G}. In this transformation, an increasing number of emerging applications demand closed-loop services of ``sensing--communication--computation--decision--control,'' making sensing rise from a peripheral auxiliary function to a key native capability of the network itself.

For example, in autonomous driving, the system must complete environmental detection, state sharing, path planning, and control execution on a millisecond time scale; in industrial Internet and smart manufacturing scenarios, the system must realize a real-time closed loop of ``monitoring--transmission--analysis--adjustment''; and in remote control and digital operation-and-maintenance scenarios, the network must continuously sense the states of physical devices and environments in order to support highly reliable feedback control \cite{Liu2022ISAC,Saad2020Vision6G}. In such closed loops, sensing is not an optional output, but the starting point and critical input of the entire service flow. If sensing depends entirely on independent systems external to the network, issues such as sensing-data return latency, interface complexity, clock synchronization, and heterogeneous data fusion may become bottlenecks that constrain closed-loop performance. Therefore, embedding sensing into the network architecture becomes an important prerequisite for achieving efficient closed-loop services.

Meanwhile, as AI/ML technologies are increasingly applied to wireless network optimization, network decisions depend more and more on an accurate understanding of environmental state. For example, intelligent beam management requires user location and movement direction information, intelligent resource scheduling requires knowledge of traffic distribution in time and space, and intelligent interference management requires identifying the locations and activity states of potential interference sources \cite{Saad2020Vision6G}. Traditional networks mainly rely on channel feedback, measurement reports, and historical statistics for optimization. Although such information is important, it is often limited in terms of environmental interpretability, real-time responsiveness, and predictive capability. ISAC addresses this limitation by natively introducing environmental sensing into the network, enabling the network to obtain richer and more direct information about the physical world, and thus providing high-value input for network intelligence. This trend directly drives the emergence of \emph{sensing-driven network intelligence} in the third stage.

\subsubsection{6G Vision Requirements for Native Capabilities}
\label{subsubsec:ch1-driving-force-6g-vision}

From a broader perspective, the vision of 6G itself requires wireless networks to go beyond the conventional role of connectivity and to possess intrinsic capabilities for real-time sensing, scene understanding, and coordinated control of the environment, targets, users, and service states \cite{Saad2020Vision6G,IMT2030Framework}. With the emergence of new scenarios such as ultra-reliable and low-latency services, native intelligence, digital twins, the low-altitude economy, and integrated space--air--ground--sea networks, communication systems are evolving from a paradigm of ``connectivity only'' toward an intrinsic capability framework that deeply integrates communications, sensing, computing, and intelligence. In this evolution, ISAC serves as a key enabling technology \cite{Gonzalez2024integrated,Liu2022ISAC}.

First, ultra-reliable and low-latency services impose stronger requirements on network predictability and determinism. Traditional wireless networks mainly rely on reactive adaptation after link degradation, which is insufficient for future services requiring extremely low latency and near-zero interruption. By acquiring information such as user location, mobility trajectory, blockage variation, and potential interference during communication, ISAC enables the network to perceive channel and topology changes in advance and to proactively perform beam management, handover, and resource allocation \cite{Liu2022ISAC,Zhang2020perceptive}. As a result, the network evolves from reactive response to proactive sensing and decision-making.

Second, native intelligence and digital twins further amplify the need for real-time environmental awareness. Intelligent networks require continuous physical-world information to support learning, inference, and optimization, while digital twins rely on accurate and timely updates of the physical environment \cite{Saad2020Vision6G,Khan2022digital}. By embedding sensing capabilities into network infrastructure, ISAC can collect information on user behavior, device status, target location, and scene dynamics while simultaneously providing communication services, thereby offering essential data support for network intelligence and digital twin systems.

In addition, emerging scenarios such as the low-altitude economy and integrated space--air--ground--sea networks are characterized by high dynamics, heterogeneous nodes, wide-area coverage, and complex propagation conditions, which require the network to support connectivity, sensing, and decision-making in a tightly coupled manner \cite{Saad2020Vision6G,IMT2030Framework}. In such scenarios, ISAC helps the network track node states, environmental conditions, and target activities in real time, thereby enhancing autonomous networking, dynamic coverage, and coordinated control.

Overall, the 6G vision no longer focuses solely on improving individual performance metrics such as data rate, latency, or coverage. Instead, it emphasizes a comprehensive intrinsic capability framework that enables the network to sense the physical world, understand the scene, predict changes, and optimize itself autonomously \cite{Liu2022ISAC,Gonzalez2024integrated,Saad2020Vision6G}. This trend indicates that sensing will become a foundational capability on par with connectivity, and ISAC will play a fundamental role in shaping the future architecture of 6G networks.

\subsection{Summary of Technical Boundaries and Core Characteristics at Each Stage}
\label{subsec:ch1-evolution-summary}

After separately discussing the three-stage evolution logic of ISAC and its major driving forces, this section provides a systematic summary of the spectrum coexistence stage, the joint design stage, and the native integration stage from the three dimensions of technical objective, design level, and evaluation metric. The purpose is to help readers grasp the relationships, differences, and progressive nature of the three stages from a holistic viewpoint. It should be emphasized that this stage-based summary is not intended to artificially separate different research directions, but rather to distill the main technical thread through which the depth of communication--sensing fusion continuously increases.

\subsubsection{Differences in Technical Objectives}
\label{subsubsec:ch1-target-differences}

From the viewpoint of technical objectives, the three stages exhibit a progressive logic from ``reducing conflict,'' to ``sharing resources,'' and then to ``forming system-level closed-loop capability.''
\begin{itemize}
    \item \textbf{Stage 1: reducing conflict and maintaining compatible operation.}  
    In the spectrum coexistence stage, communication and radar/sensing systems are still usually two independent systems. The core objective at this stage is to minimize mutual interference when the two systems share the same spectrum or operate in adjacent bands, so that the performance degradation of both sides remains within acceptable limits. In other words, the goal is not to obtain functional synergy, but to ensure compatibility and coexistence. The design philosophy of this stage can thus be summarized as ``peaceful coexistence.''
    
    \item \textbf{Stage 2: sharing resources while balancing dual-function performance.}  
    In the joint design stage, the research focus shifts to ``how to let the same platform, signal, or set of resources simultaneously serve communication and sensing'' \cite{Zhang2021ISAC6G,Hassanien2015dual}. Therefore, the core objective of this stage is no longer merely conflict reduction, but rather, through dual-functional waveform design, joint beamforming, and resource sharing mechanisms, to satisfy both communication and sensing performance requirements under given constraints and to seek the optimal tradeoff between them. The design philosophy of this stage is closer to ``cooperative win--win.''
    
    \item \textbf{Stage 3: building network-level native capability and service loops.}  
    In the native integration stage, sensing becomes part of the native capability framework of 6G and future wireless networks, jointly supporting end-to-end service processes together with communication, computing, control, and intelligence \cite{Saad2020Vision6G,Zhang2020perceptive,Cui2024integrated}. Therefore, the objective is no longer limited to link-level dual-function realization, but rises further to the construction of system-level closed-loop capability for application tasks. Through the joint support of ``sensing--communication--computation--decision--control,'' this stage aims to create holistic value for scenarios such as autonomous driving, industrial control, digital twins, and low-altitude coordination. Its design philosophy may be summarized as ``native and holistic integration.''
\end{itemize}

\subsubsection{Differences in Design Levels}
\label{subsubsec:ch1-design-level-differences}

The three stages also differ in the levels at which design is focused, showing a gradual expansion from lower to higher layers and from local to global scope.
\begin{itemize}
    \item \textbf{Stage 1: spectrum and interference management layer.}  
    In the first stage, design attention is mainly concentrated on spectrum usage and interference control. The key problem is how to realize compatible operation of communication and radar systems through frequency planning, guard-band design, power control, directional isolation, cognitive spectrum access, and interference suppression \cite{Chiriyath2017RadarCommCoexistence,Blunt2018RadarSpectrumSharing}. The design object here is the \emph{resource conflict} itself, rather than a unified system architecture.
    
    \item \textbf{Stage 2: waveform, beam, and resource joint optimization layer.}  
    In the second stage, the design scope expands into physical-layer and link-layer joint design problems, including dual-functional waveform construction, MIMO joint beamforming, transmit covariance matrix optimization, and the unified scheduling of time--frequency--space--power resources \cite{Liu2020JointRadarComm,Zhang2021ISAC6G,Sturm2011WaveformDesign}. The design object has evolved from ``avoiding conflict'' to ``forming a unified signal and resource optimization framework,'' and the main technical tools include dual-functional waveform design, communication--sensing tradeoff analysis, multiobjective optimization, and constrained optimization.
    
    \item \textbf{Stage 3: network, architecture, and service layer.}  
    In the third stage, the design scope rises further to network architecture, control-plane protocols, service orchestration, and application service loops \cite{Gonzalez2024integrated,Zhang2020perceptive,Cui2024integrated}. The key problem is no longer just how a single node can communicate and sense simultaneously, but how the entire network can natively support sensing functionality, including task scheduling for multi-node cooperative sensing, sensing-data feedback and fusion, sensing management modules within network functional entities, device--edge--cloud collaborative processing, and application-oriented service interface design. At this point, ISAC has evolved from a link-level technical problem into a system-level and service-level capability construction problem.
\end{itemize}

\subsubsection{Differences in Evaluation Metrics}
\label{subsubsec:ch1-metric-differences}

As the design objectives and system levels change, the core performance metrics of interest also differ significantly across the three stages.
\begin{itemize}
    \item \textbf{Stage 1: emphasis on mutual interference suppression and compatibility evaluation.}  
    In the spectrum coexistence stage, performance evaluation mainly revolves around the question: ``How much do the performances of the two systems degrade under coexistence conditions?'' Typical metrics include interference-to-noise ratio (INR), communication SINR under interference, bit error rate, throughput, and radar/sensing metrics such as detection probability, false alarm probability, estimation error, and interference protection margin \cite{Chiriyath2017RadarCommCoexistence,Blunt2018RadarSpectrumSharing}. These metrics reflect robustness and coexistence capability in mutual-interference environments.
    
    \item \textbf{Stage 2: emphasis on communication--sensing tradeoffs.}  
    In the joint design stage, the focus shifts to ``what jointly optimal tradeoff can be achieved between communication and sensing under given resources and constraints'' \cite{Liu2020JointRadarComm,Liu2022ISAC}. Accordingly, in addition to communication-side metrics such as rate, SINR, and bit error rate, sensing-side metrics such as detection probability, estimation accuracy, CRLB, range/velocity/angle resolution, and beampattern gain are also considered. Furthermore, Pareto boundaries, rate--estimation-accuracy regions (e.g., rate--CRLB regions), and multiobjective optimal frontiers are used to characterize the performance limits of dual-functional systems \cite{Zhang2021ISAC6G}. The central question at this stage is ``how to quantify synergy gains and performance tradeoffs.''
    
    \item \textbf{Stage 3: emphasis on system-level utility and service-loop effectiveness.}  
    In the native integration stage, link-level metrics alone are no longer sufficient to fully evaluate system value. Performance evaluation must further extend to the network and service levels \cite{Zhang2020perceptive,Cui2024integrated}. In addition to the basic communication and sensing link metrics, one must consider more comprehensive indicators such as network-level sensing coverage, sensing capacity, gains from multi-node cooperative sensing, end-to-end service latency, service availability, computing and backhaul overhead, resource utilization efficiency, and the quality of closed-loop task completion. At this stage, the key evaluation question changes from ``how does a given signal or link perform?'' to ``what overall value does ISAC bring as a native network capability to system operation and application tasks?''
\end{itemize}

To provide a more intuitive comparison among the three stages, Table~\ref{tab:stage-comparison} further summarizes their major technical characteristics.

\renewcommand{\arraystretch}{1.2}
\setlength{\tabcolsep}{4pt}

\begin{longtable}{|>{\centering\arraybackslash}p{3.0cm}|
                  >{\RaggedRight\arraybackslash}p{3.8cm}|
                  >{\RaggedRight\arraybackslash}p{3.8cm}|
                  >{\RaggedRight\arraybackslash}p{3.8cm}|}
\caption{Systematic comparison of the technical characteristics of the three stages}
\label{tab:stage-comparison} \\
\hline
\textbf{Comparison Dimension} & 
\textbf{Stage 1: Spectrum Coexistence} & 
\textbf{Stage 2: Joint Design} & 
\textbf{Stage 3: Native Integration} \\
\hline
\endfirsthead

%\hline
%\textbf{Comparison Dimension} & 
%\textbf{Stage 1: Spectrum Coexistence} & 
%\textbf{Stage 2: Joint Design} & 
%\textbf{Stage 3: Native Integration} \\
%\hline
%\endhead
%
%\multicolumn{4}{r}{\small Continued on next page} \\
%\hline
%\endfoot

\endlastfoot

\textbf{Core objective} & 
Conflict mitigation & 
Resource sharing with dual functionality & 
System-level closed-loop capability \\
\hline

\textbf{Design philosophy} & 
Peaceful coexistence & 
Cooperative dual-function design & 
Native and holistic integration \\
\hline

\textbf{Design level} & 
Spectrum/interference layer & 
Waveform/beam/\allowbreak resource layer & 
Network/architecture/\allowbreak service layer \\
\hline

\textbf{System relation} & 
Coordination of two independent systems & 
Dual-functional design on one platform & 
Native capability of one network \\
\hline

\textbf{Core metrics} & 
Interference suppression and compatibility & 
Communication--sensing tradeoff & 
System-wide utility and service value \\
\hline

\textbf{Representative techniques} & 
Spectrum sharing, interference management & 
DFRC waveform, joint beamforming & 
Cellular sensing, cooperative networking, service loop \\
\hline

\textbf{Maturity level} & 
Relatively mature & 
Rapidly developing & 
Early exploration stage \\
\hline

\end{longtable}

Finally, it should be emphasized that these three stages should not be mechanically interpreted as a strictly chronological sequence. In reality, the problems of all three stages are still being pursued in parallel in both current research and engineering practice. On the one hand, spectrum coexistence remains a long-term issue in practical deployment. On the other hand, link-level joint design is still one of the central topics in present-day ISAC research, while network-level native integration is only beginning to unfold \cite{Liu2022ISAC,Gonzalez2024integrated,Cui2024integrated}. Therefore, the three-stage classification more accurately reflects a progression in the \emph{depth of technological fusion}, \emph{level of system integration}, and \emph{capability boundary}, rather than a strictly linear historical timeline. Many practical systems contain technical elements from more than one stage at the same time, which is also an important aspect of the complexity and openness of ISAC.
