 
\section[6G Requirements, Standardization, and Scenario Requirements]{6G Requirements, Standardization, and Scenario\\ Requirements}

\subsection{Why ISAC Is Included in the 6G Capability Framework}

From 3G to 5G, the evolution of mobile communication systems was mainly driven by the improvement of communication performance.
3G enabled the development of mobile data services.
4G made mobile broadband and all-IP networking more mature.
5G further enhanced the network capabilities for enhanced mobile broadband, ultra-reliable low-latency communication, and massive machine-type communication.
As a result, key performance indicators such as data rate, transmission latency, connection density, reliability, and spectrum efficiency have been significantly improved.
These communication capabilities remain important foundations for 6G networks.
However, they are no longer sufficient to fully describe the mobile communication vision for 2030 and beyond.

In Recommendation ITU-R M.2160-0, the ITU-R describes the framework and overall objectives for the development of IMT-2030, including usage scenarios and capabilities for 2030 and beyond~\cite{ITU_M2160_2023}.
Future mobile communication systems are not expected to merely continue the pursuit of higher peak data rates, larger system capacity, and higher connection density.
Instead, 6G is expected to support the coordinated development of multiple network capabilities.
In addition to the enhancement of conventional communication capabilities, 6G also needs to support broader system objectives, such as ubiquitous connectivity, artificial intelligence, sensing capability, sustainability, security, and resilience.
This indicates that 6G should not be understood simply as a higher-rate network.
Rather, it should be regarded as a next-generation network system that supports multi-scenario, multi-functional, and multi-service coordination.

This transition is closely related to the changing role of future wireless networks.
As wireless networks are increasingly involved in transportation, industry, low-altitude airspace, urban governance, and digital twin applications, their tasks are no longer limited to bit transmission.
Many emerging services require the network to obtain information directly related to the physical world, such as target location, motion state, spatial structure, environmental variation, and service control state.
In other words, future networks need not only to ensure reliable information transmission.
They also need to acquire real-time awareness of the physical environment and use such awareness to support network optimization, service decision-making, and closed-loop control.

Traditional communication networks can evaluate link quality through channel state information, received power, signal-to-noise ratio, bit error rate, and other communication-oriented metrics.
However, these metrics mainly serve the purpose of data transmission.
They can indicate whether a link becomes better or worse, but they do not necessarily reveal the physical reasons behind the link variation.
For example, a decrease in link quality may be caused by blockage, stronger multipath propagation, target motion, device posture variation, or changes in the surrounding environment.
In conventional communication systems, these factors are usually treated as uncertainties to be compensated for.
In 6G networks, however, they may also become important sources of information for understanding the environment and target states.

In this context, the role of ISAC becomes clear.
During wireless propagation, radio signals interact with the surrounding environment through reflection, scattering, diffraction, and Doppler effects.
These propagation phenomena affect communication links.
At the same time, they also carry sensing information related to target range, velocity, angle, and environmental structure.
Conventional communication systems mainly focus on overcoming these propagation effects in order to reliably recover the transmitted information.
ISAC further exploits these effects, enabling the same wireless infrastructure to acquire environmental information while transmitting data.
Therefore, ISAC should not be regarded as simply adding a radar module beside a communication system.
Instead, it represents a new way of understanding the relationship among wireless signals, communication links, and the physical environment.

From the perspective of 6G network capabilities, the role of ISAC is not limited to a single performance indicator.
By sharing spectrum, signals, antennas, and radio-frequency platforms, ISAC can improve resource utilization efficiency.
By providing real-time environmental information for scenarios such as vehicle-road cooperation, low-altitude networks, and industrial control, it can support low-latency closed-loop services.
It can also provide environmental context for beam management, mobility prediction, resource scheduling, and edge intelligence.
Furthermore, sensing results themselves may become a new type of network service, providing basic data for localization, tracking, monitoring, imaging, and digital twin construction.

Therefore, ISAC is included in the 6G capability framework not merely because it is a new physical-layer function, but because it reflects the expansion of future network capabilities.
A 6G network is not only a higher-rate communication network.
It is also a multi-functional network that can connect, sense, and understand the physical world.
ISAC is one of the key technical paths supporting this transition.
It enables wireless networks to evolve from conventional information transmission infrastructure toward infrastructure for physical-world sensing and intelligent services.
 
\subsection{Positioning of ISAC in Global Standardization}

The need for ISAC standardization comes from the fact that communication and sensing must operate within the same wireless system.
These two functions may share spectrum, waveforms, reference signals, antenna arrays, radio-frequency chains, baseband processing resources, and network infrastructure.
Without common definitions of signals, procedures, resource configuration, and measurement interfaces, different devices and network nodes cannot reliably cooperate.
Therefore, standardization is an important basis for moving ISAC from standalone techniques to practical network capabilities.

The purpose of ISAC standardization is not to mandate identical algorithmic implementations across all systems.
Instead, it is to define the basic rules required for system interoperability.
For example, standards need to clarify which communication signals or reference signals can be used for sensing.
They also need to define how sensing tasks share time, frequency, spatial, and power resources with communication services.
In addition, sensing measurements must be represented and reported in a form that can be understood by the network.
The network also needs mechanisms to fuse sensing information from different nodes.
These issues determine whether ISAC can be deployed in networks with multiple devices, multiple nodes, and multiple scenarios.

Several standardization activities provide useful references for understanding the current positioning of ISAC.
Recommendation ITU-R M.2160-0 defines the framework and overall objectives for the future development of IMT-2030 and beyond~\cite{ITU_M2160_2023}.
It mainly provides a high-level 6G capability framework.
It does not define a specific ISAC air-interface protocol.

The 3GPP documents are more closely related to ISAC requirements and service definitions in cellular mobile communication systems.
For example, 3GPP TR 22.837 is a study report on Integrated Sensing and Communication~\cite{3GPP_TR_22837}.
It studies ISAC scenarios, requirements, and system capabilities in cellular systems.
Furthermore, 3GPP TS 22.137 is a technical specification entitled ``Integrated Sensing and Communication''~\cite{3GPP_TS_22137}.
It focuses on functional requirements and performance requirements for 5G wireless sensing services.
These documents indicate that cellular ISAC standardization is moving from conceptual discussion toward service requirement and system capability definition.

IEEE 802.11bf focuses on \acs{WLAN} sensing.
It studies how IEEE 802.11 devices and Wi-Fi signal features can be used to support sensing functions~\cite{IEEE_80211bf}.
It is not part of the cellular 6G ISAC standardization framework.
Nevertheless, it provides a representative example of how sensing capability can be introduced into an existing wireless communication standard.
This direction shows that sensing is gradually extending from dedicated radar systems to standardized wireless communication systems.

This chapter only provides a high-level positioning discussion of ISAC standardization.
Detailed standard clauses are not discussed here.
Reference signal design, sensing procedures, measurement reporting, channel models, network architecture, and test specifications will be revisited in later chapters when needed.
 

\subsection{Classification Framework of Typical Application Scenarios}

ISAC application scenarios exhibit significant differences in their underlying requirements.
Different scenarios may involve different communication objects, sensing objects, spatial scales, mobility levels, network forms, and service objectives.
Therefore, ISAC applications should not be described using a single uniform scenario model.

The purpose of scenario classification is not simply to list application names.
Rather, it is to identify the communication requirements, sensing requirements, and system constraints behind different applications.
This classification provides a basis for understanding why different ISAC scenarios may require different waveform designs, beamforming strategies, resource allocation methods, and network architectures.

\topichead{Classification by Mobility and Spatial Scale}

ISAC scenarios can first be understood from the perspectives of mobility and spatial scale.
For static or low-mobility scenarios, such as indoor monitoring, fixed equipment status sensing, and some industrial applications, the system usually pays more attention to stable observation, long-term monitoring, and deployment cost.
For high-mobility scenarios, such as vehicle-road cooperation, unmanned aerial vehicle networks, and high-speed mobile terminals, the system needs to place more emphasis on Doppler effects, target tracking, beam maintenance, latency constraints, and link reliability.

Spatial scale also has a direct impact on ISAC system design.
Local-area scenarios usually emphasize short-range sensing, high sensing accuracy, and low-cost deployment.
Cellular and wide-area scenarios pay more attention to coverage, cooperative sensing, and resource management.
Global or full-domain scenarios further involve the cooperation among heterogeneous networks in space, air, ground, and sea domains.

\topichead{Classification by Network Form}

ISAC scenarios can also be classified according to the network form.
The simplest form is single-node ISAC, where one base station, user equipment, or access point performs both communication and sensing functions.
This structure is relatively simple to implement.
It is suitable for local detection, localization, or environmental sensing.

In more complex scenarios, a single node is often limited by its coverage range, observation angle, and blockage conditions.
Multi-node, cellular, cell-free, or distributed ISAC can exploit multiple base stations, roadside units, user terminals, unmanned aerial vehicles, or edge nodes for cooperative sensing.
This makes it possible to obtain a larger sensing coverage and more observation perspectives.
However, these architectures also introduce new system issues, such as synchronization, fronthaul or backhaul transmission, information fusion, and resource coordination.

\topichead{Classification by Service Objective}

Different ISAC scenarios can further be classified according to their service objectives.
Some applications focus on environmental perception or regional state acquisition, such as area imaging, environmental monitoring, and crowd sensing.
Some applications focus on target detection, such as intruder detection, drone detection, and fall detection.
Some applications focus on localization and tracking, such as high-precision localization, vehicle tracking, and drone trajectory management.
Other applications emphasize closed-loop control or resource optimization, such as sensing-assisted beam management, sensing-assisted resource allocation, and robot coordination in smart manufacturing.
Different service objectives directly affect the system requirements on range resolution, velocity resolution, angular resolution, detection probability, latency, reliability, and data rate.

Therefore, scenario classification provides a bridge between application requirements and technical design.
Mobility determines the requirements on Doppler robustness and tracking capability.
Spatial scale affects coverage strategy and cooperative architecture.
Network form determines how sensing information is acquired and fused.
Service objective determines the priority between communication and sensing metrics.

Based on this classification framework, the next subsection further analyzes the underlying requirements of several typical application scenarios.
It also discusses how these requirements influence the design of ISAC systems.

\subsection{Requirement Analysis of Typical Application Scenarios}

The differences among typical application scenarios are essentially reflected in their communication requirements, sensing requirements, and system constraints.
The previous subsection introduced a classification framework based on mobility, spatial scale, network form, and service objective.
This subsection further discusses several representative network-level application scenarios.
The purpose is to explain why these scenarios require ISAC and how their requirements may influence system design.

\topichead{Vehicle-Road Cooperation and Intelligent Transportation}

In vehicle-road cooperation and intelligent transportation, communication and sensing are strongly coupled.
Vehicles, roadside units, base stations, and edge nodes need to exchange road information, vehicle states, control messages, and safety warnings with low latency and high reliability.
From the sensing perspective, the system needs to detect road users, obstacles, pedestrians, non-line-of-sight targets, and changes in the traffic environment.
Therefore, target detection, range estimation, velocity estimation, angle estimation, and trajectory tracking are all important sensing functions in this scenario.

The main challenges come from high mobility, complex multipath propagation, and blockage.
The sensing capability of a single vehicle is usually limited by line-of-sight conditions, sensor field of view, and occlusion.
As a result, it may be difficult for an individual vehicle to obtain complete information about the surrounding traffic environment.
With ISAC, roadside units, base stations, and vehicles can acquire environmental information during communication.
The sensed information can then be fused at edge nodes to support blockage compensation, trajectory prediction, and traffic situation awareness.
Therefore, vehicle-road cooperation requires not only single-node sensing accuracy, but also network-level cooperative sensing, low-latency processing, and robust system design.

\topichead{Low-Altitude Economy and UAV Scenarios}

Low-altitude economy and UAV scenarios usually involve UAV control, task data transmission, airspace monitoring, and multi-UAV cooperation.
The communication link should provide reliable and continuous control connectivity while also supporting the transmission of images, videos, mapping data, and other mission-related payloads.
For tasks such as cooperative UAV operation, inspection, logistics, emergency communication, and low-altitude traffic management, the communication system must also adapt to dynamic topology and air-ground cooperation.

From the sensing perspective, the system needs to continuously obtain UAV position, velocity, trajectory, surrounding obstacles, and airspace states.
Compared with conventional terrestrial cellular scenarios, low-altitude networks have clear three-dimensional spatial characteristics.
The mobility of aerial nodes is high, and both link conditions and network topology may change rapidly.
The original coverage direction, beam configuration, and interference management of terrestrial base stations may not be sufficient for low-altitude targets.
Therefore, low-altitude ISAC needs to consider wide-area coverage, continuous tracking, air-ground cooperative sensing, and lightweight deployment.
For high-speed or dense UAV scenarios, sensing results can also support beam prediction, trajectory management, and collision warning, thereby improving communication reliability and flight safety.

\topichead{Industrial Internet and Smart Manufacturing}

Industrial Internet and smart manufacturing emphasize highly reliable communication, deterministic transmission, and real-time control.
Robots, automated guided vehicles, sensors, controllers, and production equipment in factories need to work cooperatively under strict latency constraints.
Therefore, communication requirements in this scenario usually include low latency, high reliability, stable networking, and massive device access.
Unlike ordinary mobile communication services, communication failures in industrial scenarios may directly affect production processes, equipment safety, or control accuracy.

From the sensing perspective, the system needs to obtain equipment states, target positions, posture variations, process anomalies, defect information, and environmental states.
For example, robot coordination, equipment condition monitoring, defect detection, warehouse management, and production line optimization all require continuous perception of the physical environment and equipment behavior.
Industrial environments usually contain many metallic objects, complex blockages, and strong reflections.
As a result, multipath propagation and interference are often significant.
In this scenario, ISAC can integrate communication, localization, condition monitoring, and process sensing to provide real-time information for industrial control loops.
Accordingly, industrial ISAC places strong emphasis on high-precision sensing, deterministic latency, stable coverage, and fast edge processing.

\topichead{Public Safety and Smart City Scenarios}

Public safety and smart city scenarios involve wide coverage, diverse target types, and complex service forms.
Communication systems need to support wide-area connectivity, emergency coordination, massive terminal access, and information sharing across different service entities.
Sensing systems need to support regional situation awareness, target monitoring, anomaly detection, traffic flow monitoring, human activity sensing, and event warning.
In these scenarios, ISAC does not always pursue extremely high accuracy for a single target.
Instead, it often focuses on large-area, continuous, and multi-node sensing capability.

The main challenges come from the complexity of urban environments.
Buildings, traffic flows, human activities, and unexpected events may all affect system operation.
A single node is usually unable to cover a large region or accurately interpret complex events from one observation perspective.
By reusing existing communication infrastructure, ISAC can organize base stations, roadside units, terminals, and edge nodes into a distributed sensing network.
This enables wider-area situation awareness and event detection.
For public safety and smart city applications, the key requirements of ISAC include multi-node cooperation, wide-area monitoring, reliable information fusion, and service-level coordination.

\topichead{Space-Air-Ground-Sea Integrated Scenarios}

Space-air-ground-sea integrated scenarios involve a wider and more heterogeneous network environment.
Typical nodes may include satellites, UAVs, aerial platforms, terrestrial base stations, maritime platforms, and ships.
From the communication perspective, the system needs to support cross-domain connectivity, long-distance coverage, heterogeneous network cooperation, and emergency communication.
From the sensing perspective, it needs to support wide-area remote sensing, target monitoring, maritime situation awareness, airspace monitoring, disaster assessment, and environmental observation.

The main difficulties in this scenario include complex propagation environments, long link distances, large delay variations, different mobility patterns of heterogeneous nodes, and difficult synchronization and cooperation among different platforms.
Compared with terrestrial cellular networks, space-air-ground-sea integrated ISAC relies more heavily on distributed cooperation and cross-domain information fusion.
Satellites, UAVs, ground stations, and maritime nodes can collect sensing information from different heights, angles, and coverage ranges.
Communication links can then be used to exchange and fuse these data.
Therefore, ISAC in this scenario needs to support long-distance sensing, wide-area coverage, heterogeneous network cooperation, synchronization mechanisms, and full-domain integration architecture.

Overall, the above scenarios are different in system scale, mobility, network form, and service objective.
However, they all reflect a common trend.
Future networks need both information transmission capability and physical-environment sensing capability.
Different scenarios change the priority between communication and sensing.
They also influence the design of waveforms, beams, resource allocation, edge processing, and network architecture.
Therefore, ISAC system design should not only optimize a single communication metric or a single sensing metric.
Instead, it should start from the underlying requirements of specific scenarios and balance communication performance, sensing performance, deployment cost, and system complexity.

\subsection{Mapping from Scenario Requirements to Technical Design}

The previous classification of typical scenarios and the analysis of their requirement characteristics show that the differences among ISAC applications are not only reflected in the application scenarios themselves.
More fundamentally, they arise from different communication requirements, sensing requirements, and system constraints.
Scenario requirements can be regarded as an intermediate link between the 6G vision and ISAC technical design.
On the one hand, they make the general 6G requirements on connectivity, sensing, intelligence, and service capabilities more concrete.
On the other hand, they provide design guidance for waveform design, beam design, resource allocation, and network architecture.

Specifically, scenario requirements first affect the performance priorities of the system.
Some scenarios place more emphasis on communication reliability and low latency.
Some scenarios place more emphasis on sensing accuracy and detection capability.
Other scenarios focus on whether communication and sensing results can jointly support closed-loop control.
Scenario requirements also affect system architecture choices.
For example, the system may adopt single-node sensing or multi-node cooperation.
It may use a unified waveform or separated resources.
Sensing results may be processed at the edge side or fused at the central side.
Furthermore, these choices will be reflected in specific technical modules, including ISAC waveform design, MIMO and beamforming, communication-sensing resource allocation, joint receiver processing, network cooperation, and standardization interfaces.

Therefore, ISAC system design should not start only from a single communication metric or a single sensing metric.
Instead, it should start from the underlying requirements of specific scenarios.
A reasonable trade-off needs to be established among communication performance, sensing performance, deployment cost, and system complexity.
This requirement-to-design mapping also forms the basic logic for the subsequent technical chapters.
